\section{AP-E15: relaxation defect and fibre-phase purification}

AP-E15 freezes the AP-E11 action at
\begin{equation}
 W(F)=\frac12|F|^2+\frac R2|M_2(F)|^2+\frac K2|M_3(F)|^2,
 \qquad (R,K,m^2)=(1,0.35,0.12),
\end{equation}
and authorizes no further lattice scans.  For a recovery sequence with weak
complete-minor graph limit, define
\begin{equation}
 \Xi(F)=(F,\sqrt R\,M_2(F),\sqrt K\,M_3(F)).
\end{equation}
The canonical nonnegative relaxation defect measure is
\begin{equation}
 \frac12|\Xi(Du_j)|^2\dd x\stackrel{*}{\rightharpoonup}
 \frac12|\Xi(Du)|^2\dd x+\mu .
\end{equation}
Its total mass is the gap between the relaxed and naive energies, and
$\mu=0$ is equivalent to strong convergence of all three minor levels.

For the Hopf split $n=h(u)$, $a=2u^*\theta$, a compact phase sends
$a\mapsto a+2\dd\chi$ while preserving $n$, $da$, boundary data, and degree.
The exact local phase functional has second variation
\begin{align}
 D^2\mathcal F_u(\chi)[\phi,\phi]
 =\int\bigl(&|\dd\phi|^2+\tfrac R4|\dd\phi\wedge Dn|^2
 +\tfrac K{16}|\dd\phi\wedge da|^2\notag\\
 &+m^2\Re(e^{i\chi}z)\phi^2\bigr).
\end{align}
On a three-ball it is therefore strongly convex whenever
$\lambda_r=1-m^2r^2/\pi^2>0$.  If $u_j$ is a smooth fixed-degree minimizing
sequence, its optimal compact-phase energy drop satisfies
\begin{equation}
 0\leq\Delta_j(B_r)\leq\mathcal E(u_j)-I_B\to0,\qquad
 \|\dd\chi_j\|_2^2\leq2\Delta_j(B_r)/\lambda_r\to0.
\end{equation}
Thus every compact-fibre-phase-reducible vertical defect is zero.  This does
not eliminate mixed concentration produced by simultaneous oscillation of
the Hopf base.

The remaining AP-E13 cutoff defect has the exact Hopf form
\begin{equation}
 \mathfrak D_u(x,r;q)=\frac1{16r^2}\int_{B_r(x)}|u-q|^2
 (|a\wedge Dn|^2+|da|^2).
\end{equation}
At almost every Lebesgue point, with $q=u(x)$, Sobolev differentiability and
$|M_2|^2\in L^1$ give
$\mathfrak D_u=O(r^3)+o(r)\to0$.  This fixed-map limit does not commute
automatically with the recovery limit.  A singular $\mu$ can live on the
exceptional set, and a diffuse base/mixed component is not yet tied to this
estimate.  The next theorem must prove
\[
 \lim_{r\downarrow0}\limsup_j r^{-2}\int_{B_r(x)}
 |u_j-q_{j,r}|^2|M_2(Du_j)|^2=0
 \quad\text{for $\mu$-a.e.\ }x,
\]
or an equivalent sequence-uniform excess contraction.  Only after that
theorem yields full $\mu=0$, local recovery, regularity, and isolation may
the same-action bosonic Hessian be assembled.  Parallel Dirac/Callias
mathematics on a prescribed smooth Hopf base is allowed, but determinant and
portal promotion remain false.
