\section{AP-E14: fixed-map WZ decay, Morrey boundary, and Hopf div--curl test}

For every fixed complete-minor graph map, including the selected relaxed
$B=1$ representative,
\begin{equation}
 \sup_x\frac{\operatorname{dist}(\int_{B_r(x)}u^*\omega_3,
 2\pi^2\mathbb Z)^2}{r^3}
 \leq\frac{4\pi}{3}\sup_x\int_{B_r(x)}|M_3(Du)|^2=o(1).
 \label{eq:e14-wz}
\end{equation}
This is uniform absolute continuity of one fixed $L^1$ density and uses no
minimality.  It does not contradict AP-E13's scale-dependent,
non-equiintegrable cap family.

WZ decay is insufficient for the required linear Morrey estimate.  The
circle-valued cylindrical defect
\begin{equation}
 u(r,z)=(\cos\ell(r),\sin\ell(r),0,0),\qquad
 \ell(r)=\log\log(e/r),
\end{equation}
has rank-one derivative, $M_2=M_3=0$, zero WZ flux, and Dirichlet tail
$2\pi/\log(e/R)\to0$, but oscillation diameter two in every axis
neighbourhood.  It can be localized in a vacuum region without changing a
smooth exterior $B=1$ degree.  This does not prove irregularity of the
minimizer; it proves that actual relaxed minimality is the missing input.

For $u=(z,w)\in\mathbb S^3$, the Hopf variables
\begin{equation}
 n=(2\Re z\bar w,2\Im z\bar w,|z|^2-|w|^2),\qquad
 a=2u^*\theta
\end{equation}
obey $da=-n^*\omega_2$ in the stated standard orientation and give
\begin{align}
 |Du|^2&=(|a|^2+|Dn|^2)/4,\notag\\
 |M_2(Du)|^2&=(|a\wedge Dn|^2+|da|^2)/16,\notag\\
 |M_3(Du)|^2&=|a\wedge da|^2/64,\qquad
 B=(16\pi^2)^{-1}\int a\wedge da.                    \label{eq:e14-hopf}
\end{align}
Only the signed last integral has exact phase cancellation.  On $T^3$, take
\begin{equation}
 u=(e^{i\chi}\cos(t/2),e^{i\chi}\sin(t/2)),\qquad
 t=A\sin x_1,\quad\chi=B\sin x_2 .
\end{equation}
This lift has $da=a\wedge da=0$ but
\begin{equation}
 \int_{T^3}|M_2(Du)|^2=A^2B^2\pi^3/2>0.
\end{equation}
It therefore disproves a universal exact div--curl collapse of the full
positive cutoff remainder, whose exact Hopf form is
$|u-q|^2(|a\wedge Dn|^2+|da|^2)/(16r^2)$.

The AP-E14 production card passes $12/12$.  Three independently re-relaxed
compatible-action grids are stationary, admissible, and have degree
$[1,1,1]$; their maximum edge-angle quotients decrease
$3.767\to3.464\to3.316$.  This is evidence, not a continuum Morrey theorem.
The next admissible route is an inner-variation/monotonicity theory for the
lower-semicontinuous relaxation with explicit defect measure, followed by
elimination of the rank-one vertical--horizontal defect and an
$\varepsilon$-regularity theorem.  Hessian, determinant, and portal remain
closed.
