\documentclass[11pt]{article}
\usepackage[a4paper,margin=23mm]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,array,microtype,xurl,hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\RR}{\mathbb R}
\newcommand{\SSS}{\mathbb S}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\cof}{\operatorname{cof}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\osc}{\operatorname{osc}}

\title{AP-E13 Annular Target-Valued Endpoint Replacement:\\
A Wess--Zumino No-Go, a Scale-Compatible Repair,\\
and the Reverse-H\"older Closure Test}
\author{Route-F derivation ledger}
\date{20 July 2026}

\begin{document}
\maketitle

\begin{abstract}
AP-E12 asked for a target-valued annular replacement which keeps the trace on
a good sphere and makes all three squared complete-minor families
equiintegrable.  AP-E13 proves that this statement is false if ``low shell
energy'' is its only hypothesis.  For the geodesic-sphere trace
$g_\varepsilon(\omega)=(\cos\varepsilon,\sin\varepsilon\,\omega)$, take the
radially constant map on $A_{\rho,2\rho}$ and set
$\varepsilon=\sqrt\rho$.  Its first-, second-, and third-minor shell norms
are $O(\rho^2)$, $O(\rho)$, and zero.  Nevertheless every smooth
$\SSS^3$-valued filling of the trace satisfies
\[
 \int_{B_\rho}|M_3(DU)|^2\dd x
 \geq \frac{V(\varepsilon)^2}{|B_\rho|}
 \longrightarrow \frac{4\pi}{3},\qquad
 V(\varepsilon)=2\pi\left(\varepsilon-\tfrac12\sin2\varepsilon\right).
\]
The lower bound is forced by the Wess--Zumino volume modulo
$\operatorname{vol}(\SSS^3)=2\pi^2$.  Since every sphere in the shell has the
same trace, selection of a good sphere cannot remove it.  The corresponding
third-minor densities concentrate on shrinking balls and are not
equiintegrable.

A corrected positive theorem is also proved.  If a good-sphere trace lies in
a normal ball about $q$ and
$\|\log_q g\|_{L^\infty}\leq\Lambda\rho$, its geodesic contraction preserves
the trace and controls all complete-minor norms by the shell norms.  The
linear-in-$\rho$ oscillation is exactly the scale which compensates the cubic
minor.  Finally, the exact strong-quasiconvexity identity is tested as a
possible independent reverse-H\"older route.  Its highest cutoff-stress term
leaves $\rho^{-2}|u-q|^2|M_2(Du)|^2$; without a Morrey oscillation estimate or
prior higher integrability this is circular.  Thus the universal annular
lemma is disproved, the repaired conditional lemma is closed, but endpoint
graph density, regularity of the selected relaxed minimizer, the Riemann
Hessian, and determinant variation remain unauthorized.  The reproducible
scaling and quadrature card passes $9/9$.
\end{abstract}

\tableofcontents

\section{The proposed endpoint lemma and its exact meaning}

For $F\in\RR^{4\times3}$ let $M_k(F)$ be the vector of all $k$-minors.  The
complete-minor part of the AP-E11 continuum action is
\begin{equation}
 W(F)=\frac12\left(|F|^2+a_2|M_2(F)|^2+a_3|M_3(F)|^2\right),
 \qquad a_2,a_3>0.
 \label{eq:density}
\end{equation}
Write $A_{\rho,2\rho}=B_{2\rho}\setminus\overline B_\rho$ and
\begin{equation}
 E_k(u;A_{\rho,2\rho})=
 \int_{A_{\rho,2\rho}}|M_k(Du)|^2\dd x,
 \qquad M_1(Du)=Du.
 \label{eq:shell-energy}
\end{equation}
The requested universal statement would have to imply at least the following
vanishing property:

\begin{definition}[Universal vanishing annular replacement]
Whenever $u_j:A_{\rho_j,2\rho_j}\to\SSS^3$ and
$\sum_{k=1}^3E_k(u_j;A_{\rho_j,2\rho_j})\to0$, one can select
$s_j\in(\rho_j,2\rho_j)$ and find
$U_j:B_{s_j}\to\SSS^3$ with
$\operatorname{tr}U_j=u_j|_{S_{s_j}}$ such that
\begin{equation}
 \sum_{k=1}^3\int_{B_{s_j}}|M_k(DU_j)|^2\dd x\longrightarrow0.
 \label{eq:AR0}
\end{equation}
For endpoint graph density one needs more: after extension by zero to a fixed
ambient ball, the three squared-minor families should be equiintegrable.
\end{definition}

Ordinary Luckhaus interpolation controls a first-order Sobolev cost
\cite{Luckhaus1988}.  It does not contain the $L^2$ cubic-minor conclusion in
\eqref{eq:AR0}.  Trace extension for manifold-valued Sobolev maps can itself
carry critical analytic and homotopy obstructions \cite{MironescuVanSchaftingen2021}.
Here $\pi_2(\SSS^3)=0$ removes the ordinary null-homotopy obstruction, but it
does not remove the quantitative Wess--Zumino cost of a chosen null homotopy.

\section{The geodesic-cap trace}

Use polar coordinates on the unit three-sphere,
\begin{equation}
 y=(\cos\theta,\sin\theta\,\omega),
 \qquad 0\leq\theta\leq\pi,\quad\omega\in\SSS^2,
 \label{eq:s3polar}
\end{equation}
for which
\begin{equation}
 \dd s^2_{\SSS^3}=\dd\theta^2+\sin^2\theta\,\dd s^2_{\SSS^2},
 \qquad
 \omega_3=\sin^2\theta\,\dd\theta\wedge\omega_2,
 \qquad \int_{\SSS^3}\omega_3=2\pi^2.
 \label{eq:s3metric}
\end{equation}
For $0<\varepsilon<\pi/2$ define
\begin{equation}
 g_\varepsilon(\omega)
   =(\cos\varepsilon,\sin\varepsilon\,\omega).
 \label{eq:trace}
\end{equation}
Its two nonzero singular values on the unit $\SSS^2$ both equal
$\sin\varepsilon$.  Consequently
\begin{equation}
 \int_{\SSS^2}|D_\omega g_\varepsilon|^2\dd\omega
 =8\pi\sin^2\varepsilon,
 \qquad
 \int_{\SSS^2}|M_2(D_\omega g_\varepsilon)|^2\dd\omega
 =4\pi\sin^4\varepsilon.
 \label{eq:trace-norms}
\end{equation}
The oriented volume of the cap bounded by $g_\varepsilon$ is
\begin{align}
 V(\varepsilon)
 &=4\pi\int_0^\varepsilon\sin^2\theta\dd\theta
 =2\pi\left(\varepsilon-\frac12\sin2\varepsilon\right)\notag\\
 &=\frac{4\pi}{3}\varepsilon^3
   -\frac{4\pi}{15}\varepsilon^5+O(\varepsilon^7).
 \label{eq:cap-volume}
\end{align}

\section{A Wess--Zumino lower bound for every filling}

\begin{lemma}[Relative degree quantizes the filling volume]
Let $U:B_\rho\to\SSS^3$ be smooth with trace
$U|_{S_\rho}=g_\varepsilon$ after identifying
$S_\rho/\rho\simeq\SSS^2$.  Then some $k\in\mathbb Z$ satisfies
\begin{equation}
 \int_{B_\rho}U^*\omega_3=V(\varepsilon)+2\pi^2k.
 \label{eq:relative-degree}
\end{equation}
In particular, for sufficiently small $\varepsilon$,
\begin{equation}
 \left|\int_{B_\rho}U^*\omega_3\right|\geq V(\varepsilon).
 \label{eq:wz-distance}
\end{equation}
\end{lemma}

\begin{proof}
Glue $U$ to the oppositely oriented canonical geodesic cap along their common
trace.  The result is a map $\SSS^3\to\SSS^3$ of integer degree $k$.  The
integral of $\omega_3$ over the glued domain is therefore $2\pi^2k$, which
gives \eqref{eq:relative-degree} up to reversing $k$.  Since
$0<V(\varepsilon)<\pi^2$ for small $\varepsilon$, the closest element of
$V(\varepsilon)+2\pi^2\mathbb Z$ to zero is $V(\varepsilon)$.
\end{proof}

For an $\SSS^3$-valued map the three derivative columns are tangent to the
target.  Hence the scalar pullback Jacobian is the component of the Hodge
dual third-minor vector along $U$, and
\begin{equation}
 |U^*\omega_3|\leq |M_3(DU)|\dd x.
 \label{eq:jacobian-minor}
\end{equation}
Cauchy--Schwarz and \eqref{eq:wz-distance} now give the central estimate.

\begin{theorem}[Wess--Zumino filling bound]
Every trace-preserving filling above satisfies
\begin{equation}
 \boxed{\int_{B_\rho}|M_3(DU)|^2\dd x
 \geq\frac{V(\varepsilon)^2}{|B_\rho|}
 =\frac{3V(\varepsilon)^2}{4\pi\rho^3}.}
 \label{eq:filling-lower}
\end{equation}
The conclusion extends to a complete-minor graph limit for which the trace
and distributional Jacobian are stable.
\end{theorem}

\begin{proof}
Equations \eqref{eq:wz-distance} and \eqref{eq:jacobian-minor} imply
\[
 V(\varepsilon)
 \leq\int_{B_\rho}|M_3(DU)|\dd x
 \leq |B_\rho|^{1/2}
       \|M_3(DU)\|_{L^2(B_\rho)}.
\]
Squaring proves \eqref{eq:filling-lower}.  Stability under graph convergence
follows by strong $L^2$ convergence of the third-minor vector and the trace.
\end{proof}

\section{Disproof of the unconditional annular replacement}

On $A_{\rho,2\rho}$ set
\begin{equation}
 u_{\rho,\varepsilon}(r\omega)=g_\varepsilon(\omega).
 \label{eq:radial-constant}
\end{equation}
There are two tangential singular values $\sin\varepsilon/r$ and one zero
radial singular value.  Direct integration yields
\begin{align}
 E_1(u_{\rho,\varepsilon};A_{\rho,2\rho})
 &=8\pi\rho\sin^2\varepsilon,\notag\\
 E_2(u_{\rho,\varepsilon};A_{\rho,2\rho})
 &=\frac{2\pi}{\rho}\sin^4\varepsilon,
 &E_3(u_{\rho,\varepsilon};A_{\rho,2\rho})&=0.
 \label{eq:shell-exact}
\end{align}

\begin{theorem}[No universal endpoint replacement]
The assertion \eqref{eq:AR0} is false.  More strongly, low complete-minor
energy on a shell does not imply equiintegrable $L^2$ third minors for any
trace-preserving interior replacement.
\end{theorem}

\begin{proof}
Let $\varepsilon=\rho^{1/2}$ and send $\rho\downarrow0$.  Equation
\eqref{eq:shell-exact} gives
\begin{equation}
 E_1=8\pi\rho^2+O(\rho^3),\qquad
 E_2=2\pi\rho+O(\rho^2),\qquad E_3=0.
 \label{eq:critical-shell}
\end{equation}
Thus the entire shell graph energy tends to zero.  Every sphere in the shell
has exactly the trace $g_{\sqrt\rho}$, so no good-radius selection changes
the boundary data.  On a selected radius $s\in(\rho,2\rho)$, the filling
bound and \eqref{eq:cap-volume} give
\begin{equation}
 \int_{B_s}|M_3(DU)|^2\dd x
 \geq\frac{3V(\sqrt\rho)^2}{4\pi s^3}
 \geq \frac{1}{8}\left(\frac{4\pi}{3}+o(1)\right).
 \label{eq:selected-radius-bound}
\end{equation}
If the replacement is made at the inner radius $s=\rho$, the limit is
exactly $4\pi/3$.  In either case it does not tend to zero, contradicting
\eqref{eq:AR0}.  Extend $|M_3(DU)|^2$ by zero to a fixed ball.  Its integral
on the shrinking set $B_{2\rho}$ remains bounded below, so the family is not
equiintegrable.
\end{proof}

The full scale diagram is useful.  Put $\varepsilon=\rho^\alpha$.  Then
\begin{equation}
 E_1\asymp\rho^{1+2\alpha},\qquad
 E_2\asymp\rho^{4\alpha-1},\qquad
 \inf_U\int_{B_\rho}|M_3(DU)|^2\dd x
 \gtrsim\rho^{6\alpha-3}.
 \label{eq:alpha-diagram}
\end{equation}
The shell energy vanishes already for $\alpha>1/4$, whereas the forced
filling cost vanishes only for $\alpha>1/2$.  The interval
$1/4<\alpha\leq1/2$ is the previously missing endpoint obstruction window.
This does not contradict AP-E12's radial Mal\'y-dipole calculation: that
calculation studied a different interior two-hole mechanism and required
finite second-minor energy all the way to its singular core.  The present map
lives on a punctured shell and asks whether that core can be replaced.

\begin{remark}[Necessary boundary datum]
For a general trace $g:S_\rho\to\SSS^3$, let
$\mathcal V(g)\in\RR/(2\pi^2\mathbb Z)$ be its relative Wess--Zumino volume.
A necessary condition for vanishing cubic-minor filling cost is
\begin{equation}
 \frac{\dist(\mathcal V(g),2\pi^2\mathbb Z)^2}{\rho^3}\longrightarrow0.
 \label{eq:necessary-wz}
\end{equation}
The shell norm alone does not imply \eqref{eq:necessary-wz}.
\end{remark}

\section{A scale-compatible positive replacement theorem}

The no-go identifies the missing hypothesis.  The following sufficient
condition is stronger than \eqref{eq:necessary-wz}, but it controls all
three minor orders simultaneously.

\begin{theorem}[Conditional target-valued endpoint replacement]
Let $g:S_\rho\to\SSS^3$ have image in a normal ball about $q\in\SSS^3$ and
suppose
\begin{equation}
 \|\log_q g\|_{L^\infty(S_\rho)}\leq\Lambda\rho,
 \qquad \Lambda\rho<\tfrac14\operatorname{inj}(\SSS^3).
 \label{eq:linear-osc}
\end{equation}
Put
\begin{equation}
 T_1(g)=\int_{S_\rho}|D_\tau g|^2\dd S,\qquad
 T_2(g)=\int_{S_\rho}|M_2(D_\tau g)|^2\dd S.
 \label{eq:trace-costs}
\end{equation}
There is a trace-preserving $U:B_\rho\to\SSS^3$ and a constant $C$,
uniform for $\Lambda\rho$ in a fixed normal ball, such that
\begin{align}
 \int_{B_\rho}|DU|^2\dd x
 &\leq C\{\rho T_1+\Lambda^2\rho^3\},
 \label{eq:positive-one}\\
 \int_{B_\rho}|M_2(DU)|^2\dd x
 &\leq C\{\rho T_2+\Lambda^2\rho T_1\},
 \label{eq:positive-two}\\
 \int_{B_\rho}|M_3(DU)|^2\dd x
 &\leq C\Lambda^2\rho T_2.
 \label{eq:positive-three}
\end{align}
\end{theorem}

\begin{proof}
Write $v(\omega)=\log_qg(\rho\omega)$ and define the geodesic cone
\begin{equation}
 U(r\omega)=\exp_q\left(\frac r\rho v(\omega)\right),
 \qquad 0\leq r\leq\rho.
 \label{eq:geodesic-cone}
\end{equation}
It is $\SSS^3$-valued, equals $q$ at the centre, and has trace $g$.  On the
fixed normal ball, $D\exp_q$ and its exterior powers are uniformly bounded
and invertible.  Since $r/\rho$ cancels the $1/r$ in a physical angular
derivative,
\begin{equation}
 |D_rU|\leq C\Lambda,qquad
 |D_\tau U(r,\omega)|\leq C|D_\tau g(\rho\omega)|.
 \label{eq:cone-derivatives}
\end{equation}
Decomposing exterior products into radial--tangential and purely tangential
parts gives
\begin{align}
 |M_2(DU)|^2
 &\leq C\{|M_2(D_\tau g)|^2+\Lambda^2|D_\tau g|^2\},
 \label{eq:cone-m2}\\
 |M_3(DU)|^2
 &\leq C\Lambda^2|M_2(D_\tau g)|^2.
 \label{eq:cone-m3}
\end{align}
The volume-to-boundary factor in polar integration is
$\int_0^\rho r^2\dd r/\rho^2=\rho/3$.  Integrating
\eqref{eq:cone-derivatives}--\eqref{eq:cone-m3} proves
\eqref{eq:positive-one}--\eqref{eq:positive-three}.
\end{proof}

If a shell map satisfies the scale-compatible oscillation bound and
$E_k=E_k(u;A_{\rho,2\rho})$, coarea selects one radius
$s\in(\rho,2\rho)$ at which, after changing universal constants,
\begin{equation}
 T_1(u|_{S_s})\leq C\frac{E_1}{\rho},qquad
 T_2(u|_{S_s})\leq C\frac{E_2}{\rho}.
 \label{eq:good-sphere}
\end{equation}
The theorem then bounds the filling by
$C(E_1+E_2+\Lambda^2\rho^3)$ at every minor order.  For the cap family,
$\varepsilon=\Lambda\rho$ makes all three costs $O(\rho^3)$.  Thus
linear-in-radius oscillation is a clean sufficient repair.  It is not a
consequence of the assumed endpoint graph energy; the critical counterexample
has oscillation $\sqrt\rho$.

\section{Can exact strong quasiconvexity bypass the no-go?}

For $G=F^TF$, differentiation of \eqref{eq:density} gives the classical
stress
\begin{equation}
 P(F)=F+a_2\{(\tr G)F-FG\}+a_3F\cof G.
 \label{eq:stress}
\end{equation}
The singular-value representation implies
\begin{equation}
 |P(F)|\leq C\{|F|+|F||M_2(F)|+|M_2(F)||M_3(F)|\}.
 \label{eq:stress-bound}
\end{equation}
AP-E12 proved the exact ambient strong-quasiconvexity identity.  For an
actual smooth constrained minimizer, a target-valued cutoff comparison or
formal tangent first variation would therefore try to estimate the highest
stress term by
\begin{align}
 \frac{|u-q|}{\rho}|M_2(Du)||M_3(Du)|
 &\leq \eta|M_3(Du)|^2
 +\frac{C_\eta}{\rho^2}|u-q|^2|M_2(Du)|^2.
 \label{eq:cutoff-obstruction}
\end{align}
The first term is absorbable.  The second is not controlled at the endpoint:
$M_2(Du)^2$ is only in $L^1$, while Poincar\'e control of $u-q$ is not
$L^\infty$.  H\"older would require higher integrability of $M_2(Du)$, which
is the conclusion the reverse-H\"older argument is meant to prove.  An
$L^\infty$ Morrey estimate $\|u-q\|_\infty\leq c\rho$ would close the scale,
but it is precisely the additional hypothesis of the positive annular
theorem.

\begin{proposition}[Reverse-H\"older closure verdict]
The exact strong-quasiconvexity identity does not, by itself, provide a
non-circular reverse-H\"older seed for the sphere-constrained relaxed
minimizer.  A successful model-specific proof must add at least one new
ingredient which controls \eqref{eq:cutoff-obstruction}: for example a
Wess--Zumino-flux decay plus Morrey oscillation estimate, a monotonicity or
frequency formula, or a compensated Noether/Maurer--Cartan estimate.
\end{proposition}

This proposition is a boundary statement, not a proof that every possible
reverse-H\"older theorem is false.  Minimality may exclude the cap pattern for
the selected $B=1$ solution, but that requires a new model-specific theorem.
Moreover, the selected object is presently only a minimizer of the fixed-
degree lower-semicontinuous relaxation.  Until local fixed-trace recovery is
available, inserting the naive stress \eqref{eq:stress} into its weak
Euler--Lagrange equation would assume the desired conclusion.

The caution is consistent with the older Skyrme variational literature:
finite Skyrme energy maps need not be continuous, and smooth approximation
with uniformly bounded Skyrme energy was explicitly identified as an
unresolved step \cite{AucklyKapitanski2003}.  Integer degree and existence can
instead be established directly in the energy class \cite{EstebanMuller1992}.
Recent progress for the Faddeev--Skyrme Hopf map proves global minimality in
a special homogeneous large-coupling problem, but does not supply the
present $\SSS^3$ complete-minor endpoint replacement
\cite{GuerraLamyZemas2026}.
A second 2026 result characterizes $W^{1,2}$ Hopf lifts by exactness of the
pulled-back area form and constructs smooth approximations preserving that
base-map/gauge constraint \cite{GuerraLamyZemasLifting2026}.  It does not
control $L^2$ second and third minors, but it suggests an actionable change of
variables for the next reverse-H\"older attempt: decompose the $\SSS^3$ field
into its $\SSS^2$ Hopf projection and vertical gauge one-form, then test
whether \eqref{eq:cutoff-obstruction} becomes an exact div--curl pairing.

\section{Numerical verification and authorization ledger}

The independent card
\begin{center}
\texttt{route\_f/code/verify\_ap\_e13\_annular\_replacement\_reverse\_holder.py}
\end{center}
checks the exact trace norms, stable cap-volume series, Wess--Zumino lower
bound, explicit geodesic filling, and power-law slopes.  It passes $9/9$.
At the smallest production radius $\rho=10^{-8}$ with
$\varepsilon=\sqrt\rho$, the shell norm is $6.283\times10^{-8}$ whereas the
filling lower bound is $4.188790188$, converging to $4\pi/3$.  For
$\varepsilon=\rho$, all measured slopes equal three to numerical precision.

The updated decision is
\begin{equation}
 \boxed{\begin{gathered}
 C_{\rm universal\ annular}=\mathrm{false\ (disproved)},\qquad
 C_{\rm conditional\ linear\ oscillation}=\mathrm{true},\\
 C_{\rm reverse\ H\ddot{o}lder\ for\ selected\ minimizer}=\mathrm{false\ (open)},\\
 C_{D_{\rm end}}=C_{\rm classicality}=C_{\rm isolation}
 =C_{\rm Hessian}=C_{\det}=C_{\rm portal}=\mathrm{false}.
 \end{gathered}}
 \label{eq:decision}
\end{equation}
The no-go eliminates one proposed proof strategy, not the endpoint density
theorem itself.  The most efficient next target is now narrower: prove that
the selected relaxed $B=1$ minimizer has
\eqref{eq:necessary-wz} and scale-compatible trace oscillation on good
spheres, preferably from a monotonicity/frequency identity.  In parallel,
one may exploit the $\SSS^3\simeq SU(2)$ Maurer--Cartan and target-rotation
Noether structures to cancel the last term in \eqref{eq:stress-bound}; the
Hopf base/gauge split above is the first concrete formulation to test.  Only
after either route yields local recovery, classicality, and continuum
isolation is the same-action Riemann Hessian legal.

\bibliographystyle{unsrt}
\bibliography{route_f/tex/ap_e13_annular_replacement_reverse_holder}

\end{document}
