\documentclass[11pt]{article}
\usepackage[a4paper,margin=23mm]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,longtable,array}
\usepackage{enumitem}
\usepackage{xcolor,microtype}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{3em}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{gate}[proposition]{Fail-closed gate}
\theoremstyle{remark}
\newtheorem{remark}[proposition]{Remark}
\newcommand{\ii}{\mathrm i}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\cH}{\mathcal H}
\newcommand{\RR}{\mathbb R}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{AP-E5 Four-Dimensional Background-Field Gate:\\
Charged Two-Colour Lattice Action and the\\
Gauge--Meson--Ghost--Fermion \(B=1\) Hessian}
\author{Route F research note}
\date{16 July 2026}

\begin{document}
\maketitle

\begin{abstract}
We formulate a four-dimensional Euclidean lattice regularisation for testing
the charged two-colour Route-F candidate near a static \(B=1\) mesonic
background.  The gauge sector admits the Wilson action and its tree-level
Symanzik extension; the colour-singlet effective sector contains a neutral
\(SU(2)\) meson and a charge-two complex diquark.  Background gauge fixing
produces the Faddeev--Popov operator.  Two-flavour Wilson fermions with a
chiral meson insertion give an exact even--odd Schur factorisation.  We derive
the complete \emph{formal} graded Hessian and its one-loop determinant
curvature.

A deterministic \(2^4\) calculation then tests a strictly smaller
frozen-background quadratic truncation.  It verifies gauge/ghost
\(\xi\)-dependence, meson and diquark proxy spectra, a Wilson--Dirac Schur
complement, one collective fermion log-determinant curvature, a negative
control, a \(B=1\) continuum extrapolation, and Wilson versus
tree-Symanzik cutoff orders.  This is not importance sampling, dynamical
four-dimensional QC2D, or a determinant-positivity proof.  The complete
nonlinear Skyrme Jacobi operator, collective modes, continuum
renormalisation, Finkelstein--Rubinstein constraint, and global stability
remain open; every physics-promotion and Route-E portal flag remains false.
\end{abstract}

\tableofcontents

\section{Scope and logical levels}

Two-colour QCD has pseudoreal colour representations and meson--diquark
competition that cannot be imported from three-colour intuition
\cite{KogutEtAl2000,HandsEtAl2006}.  We separate:
\begin{enumerate}[label=(L\arabic*)]
\item the exact definition of a lattice action and its formal second
variation;
\item a deterministic finite-background spectrum with no ensemble average;
\item a volume- and continuum-controlled path-integral result.
\end{enumerate}
Only the first two are addressed.  Recent tensor-network work provides a
different controlled regulator in one spatial dimension, not a substitute
for this four-dimensional problem \cite{PaiAkiyamaTodo2025}.  Genuine
four-dimensional QC2D simulations on \(40^4\) and \(32^4\) lattices exist
\cite{BegunEtAl2022}, but their matter content and observables do not include
the extra charged-scalar sector or the coupled \(B=1\) Hessian required here.

\begin{gate}[Meaning of a green card]
A green card certifies the discretisation, projectors, Schur identity,
scaling tests, and negative control.  It does not certify Monte Carlo,
measure positivity, the interacting continuum phase, or quantum stability.
\end{gate}

\section{Four-dimensional gauge and ghost blocks}

\subsection{Wilson and Symanzik-compatible actions}

On a periodic lattice \(\Lambda_a\), let
\[
 \nabla_\mu^+f_x=\frac{f_{x+\hat\mu}-f_x}{a},\qquad
 \nabla_\mu^-f_x=\frac{f_x-f_{x-\hat\mu}}{a}.
\]
The provisional gauge group is \(SU(2)_c\times U(1)_g\), with links
\(V_\mu(x)\in SU(2)_c\) and \(z_\mu(x)=e^{\ii aqb_\mu(x)}\).  The Wilson
action is \cite{Wilson1974}
\begin{equation}
 S_{g,W}=\beta_c\sum_P\left(1-\frac12\Re\Tr V_P\right)
 +\beta_g\sum_P(1-\Re z_P).
 \label{eq:wilson}
\end{equation}
A tree-level L\"uscher--Weisz/Symanzik-compatible extension is
\begin{equation}
 S_{g,\mathrm{imp}}=\beta\left[
 c_0\sum_P\left(1-\frac12\Re\Tr W_P\right)
 +c_1\sum_R\left(1-\frac12\Re\Tr W_R\right)\right],
 \quad c_0+8c_1=1,
 \label{eq:symanzik}
\end{equation}
with \(c_1=-1/12\) at tree level
\cite{Symanzik1983I,LuscherWeisz1985}.  The matrix test uses Wilson
\(c_1=0\); a separate free dispersion test checks the improved branch.
This establishes compatibility, not an interacting improved simulation.
Here \(W\) denotes either gauge factor in its own defining representation;
Eq.~\eqref{eq:symanzik} is not a mixed \(SU(2)_c\)--\(U(1)_g\) plaquette.

\subsection{Quadratic gauge fixing and FP cancellation}

Expanding \(V_\mu=e^{\ii aA_\mu^aT^a}\) and adding
\[
 S_{\mathrm{gf}}=\frac1{2\xi}\sum_x
 \left(\nabla_\mu^-A_\mu^a\right)^2
\]
gives
\begin{equation}
 K_{\mu\nu}^{ab}(p)=\delta^{ab}\left[
 \widehat p^2\delta_{\mu\nu}+
(\xi^{-1}-1)\widehat p_\mu\widehat p_\nu^\ast\right],
 \quad
 \widehat p_\mu=\frac{e^{\ii ap_\mu}-1}{a}.
 \label{eq:gauge-kernel}
\end{equation}
Every \(p\ne0\) has three transverse eigenvalues \(\widehat p^2\) and one
longitudinal eigenvalue \(\widehat p^2/\xi\).  Background covariant gauge
has
\[
 M_{\mathrm{FP}}^{ab}=-\overline D_\mu^{ac}D_\mu^{cb};
\]
at the tested trivial gauge background it is
\begin{equation}
 M_{\mathrm{FP}}^{ab}=-\delta^{ab}\nabla_\mu^-\nabla_\mu^+.
 \label{eq:fp}
\end{equation}
Removing the constant ghost and four gauge torons, one generator obeys
\begin{equation}
 \frac12\log\det'K_A(\xi)-\log\det'M_{\mathrm{FP}}
 =
 \frac12\log\det'K_A(1)-\log\det'M_{\mathrm{FP}}
 -\frac{V-1}{2}\log\xi .
 \label{eq:xi}
\end{equation}
The final term is background independent and drops out of normalised
background differences.  Individual gauge eigenvalues are not
gauge independent.

\section{Charged meson--diquark sector}

\subsection{\texorpdfstring{Action and \(B=1\) embedding}{Action and B=1 embedding}}

Let \(U_x\in SU(2)\) be neutral and \(\Delta_x\in\mathbb C\) carry
\(q_\Delta=2\).  A compatible EFT is
\begin{align}
 S_{\chi\Delta}
 =&\frac{f^2a^2}{4}\sum_{x,\mu}
 \Tr[(U_{x+\hat\mu}-U_x)^\dagger(U_{x+\hat\mu}-U_x)]
 +S_{\mathrm{Sk},a}[U]\nonumber\\
 &+\frac{f^2m_\pi^2a^4}{2}\sum_x(2-\Tr U_x)
 +a^2\sum_{x,\mu}|z_\mu(x)^2\Delta_{x+\hat\mu}-\Delta_x|^2\nonumber\\
 &+a^4\sum_x\left[
 (m_\Delta^2+\chi\rho_B(x))|\Delta_x|^2
 +\lambda_\Delta|\Delta_x|^4\right].
 \label{eq:eft}
\end{align}
\(S_{\mathrm{Sk},a}\) is an explicitly chosen lattice transcription of the
Skyrme term \cite{Skyrme1961}; different transcriptions have different
finite-\(a\) Hessians.

The sampled static hedgehog is
\begin{equation}
 \overline U(\bm x)=\cos F(r)\mathbf1+
 \ii\sin F(r)\widehat{\bm x}\cdot\bm\tau,\qquad
 F(r)=2\tan^{-1}\left[\frac Rr e^{-r^2/(2R^2)}\right].
 \label{eq:hedgehog}
\end{equation}
It has \(F(0)=\pi,F(\infty)=0\) and orientation
\begin{equation}
 B=-\frac1{2\pi^2}\int_{\RR^3}
 \det(n,\partial_1n,\partial_2n,\partial_3n)\,\mathrm d^3x=+1,
 \quad n=(\cos F,\widehat{\bm x}\sin F).
 \label{eq:baryon}
\end{equation}
Topology is measured on open grids and extrapolated in \(a^2\).  The
\(2^4\) Hessian only samples the same analytic background; it does not
pretend that two spatial sites resolve topology.

\subsection{Exact formal versus tested meson Hessian}

Choose tangent frames \(E_x:\RR^3\to T_{n_x}S^3\) and write
\[
 n_x(\eta)=n_x+E_x\eta_x-\tfrac12n_x|\eta_x|^2+\mathcal O(\eta^3).
\]
The exact nonlinear lattice Jacobi block is
\begin{equation}
 (K_\pi)_{xi,yj}
 =\left.\frac{\partial^2}{\partial\eta_x^i\partial\eta_y^j}
 (S_\chi+S_{\mathrm{Sk},a})[n(\eta)]\right|_{\eta=0}.
 \label{eq:exact-jacobi}
\end{equation}
It contains connection, target-curvature, mass-curvature, and every Skyrme
second variation.  The finite certificate tests only the declared positive
frozen-background Gauss--Newton block
\begin{equation}
 S_{\pi,\mathrm{test}}^{(2)}
 =\frac12\sum_{\langle xy\rangle}|\eta_y-T_{yx}\eta_x|^2
 +\frac12\sum_x[m_\pi^2+\kappa_\pi\rho_B(x)]|\eta_x|^2,
 \label{eq:meson-test}
\end{equation}
where \(T_{yx}\in SO(3)\) is Levi--Civita parallel transport on \(S^3\).
Proxy positivity is therefore not reported as positivity of
Eq.~\eqref{eq:exact-jacobi}.

\subsection{Charge-two diquark Hessian}

At \(\overline\Delta=0\), the two real components share
\begin{equation}
 K_\Delta=-D_\mu^{(2)-}D_\mu^{(2)+}
 +m_\Delta^2+\chi\rho_B(x).
 \label{eq:diquark}
\end{equation}
Because \(D_\mu\Delta\) is linear in \(b_\mu\) and \(\Delta\),
\(K_{b\Delta}|_{\overline\Delta=0}=0\).  A condensed phase instead has
gauge--Goldstone mixing and requires an \(R_\xi\) treatment.

\section{Wilson fermions and Schur reduction}

\subsection{Two-flavour operator}

For colour doublets and two flavours, use \cite{WilsonFermion1977}
\begin{align}
 D_{xy}
 =&[m_0+4r/a+y_s\sigma_x+
 \ii y_p\gamma_5\bm\tau\cdot\bm\pi_x]\delta_{xy}\nonumber\\
 &-\frac1{2a}\sum_\mu[
 (r-\gamma_\mu)W_\mu(x)\delta_{x+\hat\mu,y}
 +(r+\gamma_\mu)W_\mu^\dagger(x-\hat\mu)
 \delta_{x-\hat\mu,y}].
 \label{eq:wilson-dirac}
\end{align}
The tested matrix sets colour and Abelian links to identity.  Its
\(4\) spin times \(2\) flavour components already contain \(N_f=2\);
there is no extra flavour multiplier in the log determinant.  One
\(128\times128\) spin--flavour matrix is diagonalised, and the two trivial
colour copies are recorded as a degeneracy.  This is not a measure-positivity
argument.

A standard Wilson kernel can seed an overlap construction
\cite{Neuberger1998}, but only after an admissibility/domain-wall gap and
index analysis.  Neither follows from a single finite singular value.

\subsection{Exact even--odd identity}

Even lattice extents make hopping bipartite:
\begin{equation}
 D=\begin{pmatrix}D_{ee}&D_{eo}\\D_{oe}&D_{oo}\end{pmatrix},\qquad
 S_e=D_{ee}-D_{eo}D_{oo}^{-1}D_{oe}.
 \label{eq:schur}
\end{equation}
Block elimination gives
\begin{equation}
 \det D=\det D_{oo}\det S_e,
 \label{eq:schur-det}
\end{equation}
\begin{align}
 S_ex_e&=b_e-D_{eo}D_{oo}^{-1}b_o,\nonumber\\
 x_o&=D_{oo}^{-1}(b_o-D_{oe}x_e).
 \label{eq:schur-solve}
\end{align}
Both complex determinant phase and the solution are checked against the
unreduced matrix.

\section{Formal graded Hessian and one-loop curvature}

Let \(\Phi=(A_\mu^a,b_\mu,\eta^i,d_1,d_2)\) and expand about
\((0,0,\overline U,0,0)\).  Since a bosonic fluctuation times a fermion
bilinear is cubic at \(\overline\psi=0\), the classical graded Hessian is
\begin{equation}
 \cH_{\mathrm{cl}}=
 \left(
 \begin{array}{ccccc|cc}
 K_{AA}&K_{Ab}&K_{A\pi}&K_{Ad_1}&K_{Ad_2}&0&0\\
 K_{bA}&K_{bb}&K_{b\pi}&K_{bd_1}&K_{bd_2}&0&0\\
 K_{\pi A}&K_{\pi b}&K_\pi&K_{\pi d_1}&K_{\pi d_2}&0&0\\
 K_{d_1A}&K_{d_1b}&K_{d_1\pi}&K_\Delta&0&0&0\\
 K_{d_2A}&K_{d_2b}&K_{d_2\pi}&0&K_\Delta&0&0\\ \hline
 0&0&0&0&0&0&D\\
 0&0&0&0&0&-D^T&0
 \end{array}\right),
 \label{eq:super-hessian}
\end{equation}
plus \(\overline cM_{\mathrm{FP}}c\).  In the tested neutral-meson,
\(\overline\Delta=0\), trivial-gauge background, bosonic off-diagonal
blocks vanish at tree level.  Equation~\eqref{eq:super-hessian} is the
complete \emph{formal} block structure; the numerical operator substitutes
Eq.~\eqref{eq:meson-test} for the exact nonlinear \(K_\pi\).

At one loop,
\begin{equation}
 \Gamma^{(1)}=\frac12\log\det'K_B-\log\det'M_{\mathrm{FP}}
 -\Re\log\det D_{N_f=2}.
 \label{eq:one-loop}
\end{equation}
For coordinates \(q_i\),
\begin{equation}
 \partial_i\partial_j\Gamma_f^{(1)}
 =\Re\Tr[D^{-1}D_iD^{-1}D_j-D^{-1}D_{ij}].
 \label{eq:curvature}
\end{equation}
The trace includes both flavour components and, in the formal microscopic
operator, both colours.  The numerical trivial-colour-link test evaluates one
colour copy; its full two-colour curvature is exactly twice the displayed
one-copy result.  For \(D(t)=D+tQ\), the tested identity is
\begin{equation}
 \Gamma_{f,\,\mathrm{one\ colour}}''(0)
 =\Re\Tr(D^{-1}QD^{-1}Q),
 \label{eq:trace-test}
\end{equation}
not the full one-loop multi-field Hessian.

\section{Zero modes and global obstructions}

\begin{enumerate}[label=(Z\arabic*)]
\item Constant ghosts and gauge torons are removed by primed determinants.
\item An exact infinite-volume soliton has translations and isorotations.
  Finite volume, anisotropy, and pinning lift them; the positive test block
  cannot count them.
\item A nonzero Wilson singular value is not an index.  Spectral flow or an
  admissible overlap construction is required.
\item A nonnegative local Hessian does not exclude finite-amplitude
  unwinding.  Coarse lattices do not preserve topology without a controlled
  admissibility or continuum argument.
\end{enumerate}
The Finkelstein--Rubinstein sign concerns the fundamental group of physical
configuration space and its quantisation, not an eigenvalue
\cite{FinkelsteinRubinstein1968}.

\section{Deterministic numerical certificate}

The finite benchmark uses a periodic \(2^4\) lattice, \(L=2.4\), \(R=1.2\),
\(m_\pi^2=0.25\), \(\kappa_\pi=0.18\), \(m_\Delta^2=0.81\),
\(\chi=-0.30\), \(r=1\), \(m_0=0.65\), \(y_s=0.20\), and \(y_p=0.16\).
It is deliberately small so every determinant is directly reproducible.

\subsection{Topology and bosonic spectra}

The open-grid estimator uses the larger topology box \(L_B=6.4\) at
\(N_s=17,25,33,49,65\), fitted quadratically in \(a^2\) using the last
four points, and gives
\[
 B(0)=0.999981468235.
\]
The \(2^4\) blocks give
\begin{align}
 \lambda_{\min}(K_{\pi,\mathrm{test}})&=0.621297848377,\nonumber\\
 \lambda_{\min}(K_\Delta)&=0.694069172619,\nonumber\\
 \lambda_{\min}(K_\Delta^{\mathrm{negative\ control}})
 &=-0.349308273811.
 \label{eq:numbers-boson}
\end{align}
The control changes only \(\chi:-0.30\mapsto-3.00\); its negative mode
proves the sign audit can fail.

\subsection{Gauge, fermion, and scaling residuals}

The maximum corrected residual in Eq.~\eqref{eq:xi} for
\(\xi=0.5,0.7,1,2\) is \(1.42\times10^{-14}\).
The Wilson matrix has
\[
 \sigma_{\min}(D)=0.702570765924.
\]
The determinant-log, determinant-phase, and Schur-solve residuals are
\[
 4.26\times10^{-14},\qquad
 5.19\times10^{-17},\qquad
 6.30\times10^{-16}.
\]
The trace/finite-difference relative discrepancy in
Eq.~\eqref{eq:trace-test} is \(1.32\times10^{-8}\).

At fixed physical \(L\),
\begin{align}
 \widehat p_W^2
 &=\frac4{a^2}\sin^2\frac{ap}{2}
 =p^2-\frac{a^2p^4}{12}+\mathcal O(a^4),\nonumber\\
 \widehat p_{\mathrm{imp}}^2
 &=\widehat p_W^2+\frac{a^2}{12}(\widehat p_W^2)^2
 =p^2-\frac{a^4p^6}{90}+\mathcal O(a^6).
 \label{eq:dispersion}
\end{align}
The \(N=32,64\) observed orders are
\[
 p_W=1.99860957,\qquad
 p_{\mathrm{imp}}=3.99627578.
\]
This tests free quadratic scaling, not interacting renormalisation.

\section{Status table and exact fail-closed keys}

\begin{longtable}{@{}L{0.43\textwidth}L{0.14\textwidth}L{0.35\textwidth}@{}}
\toprule
Claim & Status & Reason\\
\midrule
\endfirsthead
\toprule
Claim & Status & Reason\\
\midrule
\endhead
Wilson/Symanzik-compatible action & defined &
Equations \eqref{eq:wilson}--\eqref{eq:eft}.\\
Gauge/ghost projectors and \(\xi\) law & finite pass &
Prime spectra test Eq.~\eqref{eq:xi}.\\
Wilson even--odd Schur algebra & finite pass &
Determinant and solve identities agree.\\
Complete nonlinear \(B=1\) Hessian & open &
The test uses Eq.~\eqref{eq:meson-test}, not
Eq.~\eqref{eq:exact-jacobi}.\\
Dynamical four-dimensional QC2D phase & open &
No ensemble, importance sampling, or thermodynamic limit.\\
Positive fermion measure & open &
A singular value is not an antiunitary/global-form proof.\\
FR and finite-amplitude stability & open &
Require configuration-space topology and global minimax analysis.\\
Degree-one Route-E portal & blocked &
Preceding microscopic and global gates remain false.\\
\bottomrule
\end{longtable}

\begin{gate}[Machine-readable promotion boundary]
The JSON card sets each of the following exact keys to \texttt{false}:
\begin{itemize}[leftmargin=1.2em,itemsep=0pt,topsep=2pt]
\item \path{importance_sampling_or_Monte_Carlo_performed}
\item \path{dynamical_4d_lattice_QC2D_phase_established}
\item \path{fermion_determinant_positivity_proven}
\item \path{complete_nonlinear_gauge_meson_ghost_fermion_Hessian_computed}
\item \path{Skyrme_Jacobi_translation_isorotation_zero_modes_resolved}
\item \path{one_loop_renormalised_continuum_limit_established}
\item \path{Finkelstein_Rubinstein_constraint_derived}
\item \path{finite_amplitude_global_stability_established}
\item \path{degree_one_route_E_portal_allowed}
\item \path{physics_promotion_allowed}
\end{itemize}
\end{gate}

\section{Three routes forward}

\begin{enumerate}[label=(R\arabic*)]
\item \textbf{Full classical Jacobi route.}
Choose one explicit lattice Skyrme transcription, relax the \(B=1\)
background at each \(a,L\), assemble its exact sparse second variation,
project gauge, translation, and isorotation directions, and extrapolate all
low modes.
\item \textbf{Dynamical QC2D route.}
First prove the antiunitary symmetry and measure sign for the actual charges
and global form.  Then use HMC or an independently validated alternative,
multiple spacings and volumes, scale setting, and correlator diquark gaps.
\item \textbf{Fermion/index route.}
Establish link admissibility, compute overlap spectral flow in the relaxed
\(B=1\) background, determine the Callias/APS determinant line, and combine
its curvature with the projected bosonic Jacobi operator and FR quantisation.
\end{enumerate}

\section{Reproducibility}

The deterministic verifier is
\texttt{route\_f/code/verify\_ap\_e5\_4d\_qc2d\_lattice\_hessian.py}.
It writes JSON and Markdown cards, records source hashes and library versions,
uses seed \(20260716\) only for a Schur-solve right-hand side, and exits
nonzero if any declared check fails.

\bibliographystyle{unsrt}
\bibliography{route_f/tex/ap_e5_4d_qc2d_lattice_hessian}
\end{document}
