\documentclass[11pt]{article}
\usepackage[a4paper,margin=22mm]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,longtable,array}
\usepackage{enumitem}
\usepackage{xcolor,microtype,xurl}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{3em}
\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{gate}[theorem]{Fail-closed gate}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\RR}{\mathbb R}
\newcommand{\SSS}{\mathbb S}
\newcommand{\cB}{\mathcal B}
\newcommand{\cE}{\mathcal E}
\newcommand{\cT}{\mathcal T}
\newcommand{\cF}{\mathcal F}
\newcommand{\dd}{\mathrm d}
\newcommand{\TP}{\mathrm{TP}}
\newcommand{\ezer}{e_0}

\title{AP-E9 Scaling Trichotomy and Regulator-Stability Audit:\\
Equicoercivity, Gamma Limits, Alternative Triangulations,\\
and Translated Starts}
\author{Route F research note}
\date{18 July 2026}

\begin{document}
\maketitle

\begin{abstract}
This note resolves the first mathematical layer left open by AP-E8 and gives
a negative result for the stronger layer.  On a fixed physical box, the
original coordinate-edge Dirichlet term already makes the full discrete
action equicoercive in strong $L^2\times L^2$, independently of the barrier
scaling.  This compactness is too weak to close a degree sector.  Writing
$d_a=1-\epsilon_a$, $w_a=\gamma_a a$, and
$R_a=\gamma_a a^2/d_a^2$, the logarithmic barrier has an exact Lambert-
$W$ edge-margin bound and the global estimate

\[
 b_{\epsilon_a}(n_x\!\cdot n_y)
 \ge \frac{|n_x-n_y|^4}{8d_a^2}.
\]

For fixed $\epsilon$ and $\gamma(a)=c a^{-p}$, uniform distance from the
edge floor requires $p\ge1$, whereas the barrier disappears on smooth
fields only for $p<2$.  Hence $1\le p<2$, with the minimal choice
$p=1$, is the unique edge-interior and smooth-vanishing power window.
Nevertheless $R_a\to0$ supplies no $C^0$ compactness and the explicitly
embedded barrier-only Gamma limit forgets trace and degree.  At the critical
value $p=2$, the barrier does give $W^{1,4}$ compactness and closes degree.
Its raw six-tetrahedron and checkerboard five-tetrahedron Cauchy--Born
quartics are not scalar multiples.  The actual finite-$R$ Gamma density,
however, requires a periodic homogenized cell problem and is not identified
with either raw quartic in this note.

This is a no-free-lunch theorem for the AP-E8 barrier: no scaling makes that
barrier both continuum-vanishing and, by itself, degree-sector compact.  A
full Gamma theorem for the same-action Skyrme model is therefore reduced to
a precise remaining question about compactness of the discrete Skyrme
minors and density of smooth fixed-degree recovery sequences.  The
accompanying card tests the recommended $p=1$ trajectory, the critical
$p=2$ control, two checkerboard five-tetrahedron meshes, translated starts,
and enlarged $(a,L)$ ranges.  The physical Hessian and determinant variation
remain prohibited unless those tests and the missing minor-compactness
theorem produce one regulator-stable continuum background.
\end{abstract}

\tableofcontents

\section{Claim ledger and notation}

Let $\Omega\subset\RR^3$ be a fixed cube and let $a\downarrow0$ run over
shape-regular cubic grids.  A conforming tetrahedral complex $\cT_a$ is
placed on every grid, and $\cE_a$ denotes the unique unordered vertex pairs
that occur together in at least one tetrahedron.  The nodal variables are

\[
 n_x\in\SSS^3,\qquad s_x\in\RR,
\]

with exact vacuum boundary data $n=\ezer=(1,0,0,0)$ and $s=1$.  The AP-E8
functional is

\begin{equation}
 \cF_a[n,s]
 =E_a[n,s]+\cB_a[n],\qquad
 \cB_a[n]=w_a\sum_{\{x,y\}\in\cE_a}
 b_{\epsilon_a}(n_x\cdot n_y),
 \label{eq:functional}
\end{equation}

where

\begin{equation}
 b_\epsilon(q)=
 \begin{cases}
 -\log\dfrac{q-\epsilon}{1-\epsilon}
 +\dfrac{q-1}{1-\epsilon},&q>\epsilon,\\[5pt]
 +\infty,&q\le\epsilon.
 \end{cases}
 \label{eq:barrier}
\end{equation}

The base action $E_a$ is the AP-E7 coordinate-difference (n+s) action,
including its nonnegative Skyrme-minor, breathing-mass, and pion-mass terms.
We separate four statements that must not be conflated:

\begin{enumerate}[label=(\roman*)]
\item ordinary $L^2$ equicoercivity of all bounded sublevels;
\item uniform distance from the barrier floor;
\item compactness strong enough to preserve normalized-affine degree;
\item Gamma convergence of the complete base-plus-barrier action.
\end{enumerate}

This note proves (i), gives a sharp answer to (ii), proves the barrier
compactness regimes controlling (iii), and gives a conditional reduction
rather than an unsupported identification for (iv).

\section{Exact barrier calculus}

Put

\begin{equation}
 d_a:=1-\epsilon_a,\qquad
 w_a:=\gamma_a a,\qquad
 R_a:=\frac{\gamma_a a^2}{d_a^2}
      =\frac{w_a a}{d_a^2}.
 \label{eq:three-scales}
\end{equation}

For one admissible edge define

\begin{equation}
 x_e:=\frac{q_e-\epsilon_a}{d_a}\in(0,1],
 \qquad
 z_e:=1-x_e
 =\frac{1-q_e}{d_a}
 =\frac{|n_x-n_y|^2}{2d_a}.
 \label{eq:xz}
\end{equation}

Then the dependence on $\epsilon_a$ is isolated:

\begin{equation}
 b_{\epsilon_a}(q_e)=\phi(x_e),\qquad
 \phi(x):=-\log x-1+x.
 \label{eq:phi}
\end{equation}

\begin{lemma}[Sharp elementary bounds]
For $0\le z<1$,
\begin{equation}
 \phi(1-z)=\sum_{k=2}^{\infty}\frac{z^k}{k},\qquad
 \frac{z^2}{2}\le\phi(1-z)
 \le\frac{z^2}{2(1-z)}.
 \label{eq:phi-bounds}
\end{equation}
Consequently every admissible edge obeys the global lower bound
\begin{equation}
 \boxed{
 b_{\epsilon_a}(n_x\cdot n_y)
 \ge\frac{|n_x-n_y|^4}{8d_a^2}.}
 \label{eq:quartic-lower}
\end{equation}
\end{lemma}

\begin{proof}
The Taylor series of $-\log(1-z)-z$ gives the equality and lower bound.
For the upper bound, $1/k\le1/2$ for $k\ge2$, hence

\[
 \sum_{k=2}^{\infty}\frac{z^k}{k}
 \le\frac12\sum_{k=2}^{\infty}z^k
 =\frac{z^2}{2(1-z)}.
\]

Substituting $z=|n_x-n_y|^2/(2d_a)$ proves
Eq.~\eqref{eq:quartic-lower}.
\end{proof}

\section{Sharp bounded-sublevel edge margin}

Let $W_0$ be the principal real branch of Lambert $W$ and define

\begin{equation}
 \chi(r):=-W_0(-e^{-1-r}),\qquad r\ge0.
 \label{eq:chi}
\end{equation}

Because $\phi$ decreases from $+\infty$ to zero on $(0,1]$,
$\phi(\chi(r))=r$.

\begin{theorem}[Exact positive-sublevel margin]
Fix $C>0$.  If $\cB_a[n]\le C$, then every barrier edge satisfies
\begin{equation}
 x_e\ge\chi(C/w_a),\qquad
 q_e-\epsilon_a\ge d_a\chi(C/w_a)
 \ge d_a e^{-1-C/w_a}.
 \label{eq:margin}
\end{equation}
For every fixed $C>0$, uniform relative interiority
$x_e\ge\delta_C>0$ on the $C$-sublevels holds if and only if
\begin{equation}
 \inf_a w_a>0.
 \label{eq:w-condition}
\end{equation}
Uniform absolute interiority $q_e-\epsilon_a\ge\delta_C>0$ additionally
requires and is implied by $\inf_a d_a>0$.
\end{theorem}

\begin{proof}
Nonnegativity of every summand gives
$w_a\phi(x_e)\le C$, and inversion gives the first inequality.  Since
$\phi(x)=-\log x-1+x\ge-\log x-1$, the same sublevel inequality gives
$x_e\ge e^{-1-C/w_a}$.  If $w_a\ge w_*>0$, the right-hand side is a
positive number depending only on $C,w_*$.  Multiplication by
$d_a\ge d_*>0$ proves the absolute statement.

For necessity, pass to any subsequence on which $w_a\to0$.  Choose one
interior vertex in the exact
vacuum collar and leave all other collar vertices equal to $\ezer$.  Rotate
that vertex on a great circle so that, for a fixed $\alpha>0$ chosen smaller
than $C$ divided by twice the maximum incident-edge count,

\[
 n_z\cdot\ezer=\epsilon_a+d_a e^{-\alpha/w_a}.
\]

The number of incident co-tetrahedral edges is bounded independently of
$a$, and each contributes

\[
 w_a\phi(e^{-\alpha/w_a})
 =\alpha-w_a+o(w_a).
\]

The coordinate-edge Dirichlet cost is $O(a)$, the local potential cost is
$O(a^3)$, and every affected forward Skyrme minor has rank at most one and
therefore vanishes.  Thus the field lies in the prescribed $C$-sublevel for
all sufficiently small $a$ while the relative edge margin tends to zero.
For absolute necessity, if $d_a\to0$, the vacuum itself has zero barrier and
$q_e-\epsilon_a=d_a\to0$.
\end{proof}

\begin{remark}
The restriction $C>0$ is essential to the equivalence: on the zero sublevel
every connected-edge value has $x_e=1$, independently of $w_a$.
\end{remark}

\begin{remark}[Margin is not the no-zero bound]
If $\inf_a\epsilon_a>-1/3$, every finite-energy tetrahedron still obeys
\begin{equation}
 \left\|\sum_{i=0}^3\lambda_i n_i\right\|^2
 \ge\epsilon_a+(1-\epsilon_a)\sum_i\lambda_i^2
 \ge\frac{1+3\epsilon_a}{4}>0.
 \label{eq:no-zero}
\end{equation}
Hence $w_a\to0$ destroys uniform distance from the artificial barrier
floor, not the definition of degree on each individual grid.
\end{remark}

\section{Ordinary equicoercivity is already present}

Let $I_a$ denote the affine interpolant on any of the finitely many
shape-regular triangulation families used below.

\begin{theorem}[Fixed-box $L^2$ equicoercivity]
Assume, as in the declared AP-E7 action, that the coordinate-edge Dirichlet
part is bounded below by
\begin{equation}
 c_Da\sum_{xy}\bigl(|n_x-n_y|^2+|s_x-s_y|^2\bigr)
 \label{eq:base-coercivity}
\end{equation}
with a mesh-independent $c_D>0$.  On a fixed bounded cube with the declared
boundary data, the family
$\{\cF_a\}$ is equicoercive in strong
$L^2(\Omega;\RR^4)\times L^2(\Omega)$ for every positive choice of
$\gamma_a$ and every $\epsilon_a\in(-1/3,1)$.
\end{theorem}

\begin{proof}
Shape regularity gives a mesh-independent constant $C_T$ such that

\begin{equation}
 \|\nabla I_an_a\|_{L^2}^2+
 \|\nabla I_as_a\|_{L^2}^2
 \le C_T a\sum_{\text{coordinate edges }xy}
 \bigl(|n_x-n_y|^2+|s_x-s_y|^2\bigr)
 \le \frac{C_T}{c_D}\cF_a.
 \label{eq:H1-control}
\end{equation}

The first $L^2$ norm is bounded because the nodal values have unit norm.
For $s_a-1$, either Poincare's inequality and the exact boundary value or
the positive breathing-mass term supplies the $L^2$ bound.  Rellich
compactness gives strong $L^2\times L^2$ precompactness.  Finally,

\[
 \int_\Omega\operatorname{dist}(I_an_a,\SSS^3)^2\dd x
 \le C a^2\|\nabla I_an_a\|_{L^2}^2\longrightarrow0,
\]

so the limiting field is sphere-valued almost everywhere.  The barrier is
nonnegative and therefore cannot weaken these estimates.
\end{proof}

\begin{remark}
Strong $L^2$ convergence does not preserve the degree of a three-
dimensional sphere-valued map.  Calling Eq.~\eqref{eq:H1-control}
``topological equicoercivity'' would therefore be incorrect.
\end{remark}

\section{Smooth expansion and the power-law window}

Suppose $n\in C^3(\overline\Omega,\SSS^3)$, and let $S_an$ denote nodal
sampling.  For an edge $y=x+av$,

\[
 1-n(x)\cdot n(x+av)
 =\frac{a^2}{2}|D_vn(x)|^2+O(a^3).
\]

If $a^2/d_a\to0$, Eqs.~\eqref{eq:phi-bounds}--\eqref{eq:xz} and a Riemann-
sum estimate give

\begin{proposition}[Smooth-field asymptotics]
For a periodic shape-regular triangulation family,
\begin{equation}
 \cB_a[S_an]
 =\frac{R_a}{8}\int_\Omega Q_{\cT}(\nabla n)\dd x
 +O\!\left(R_a\left(a+\frac{a^2}{d_a}\right)\right),
 \label{eq:smooth-expansion}
\end{equation}
where $Q_{\cT}$ is the sum of $|D_vn|^4$ with the asymptotic edge
direction densities of the selected mesh.
\end{proposition}

For the AP-E8 uniform positive Freudenthal split,

\begin{equation}
 Q_{6,+}(A)=
 \sum_{i=1}^3|Ae_i|^4
 +\sum_{1\le i<j\le3}|A(e_i+e_j)|^4
 +|A(e_1+e_2+e_3)|^4.
 \label{eq:Q6}
\end{equation}

For the checkerboard five-tetrahedron mesh, each face-diagonal sign occurs at
density one half and there is no body diagonal, so

\begin{equation}
 Q_5(A)=\sum_{i=1}^3|Ae_i|^4
 +\frac12\sum_{1\le i<j\le3}
 \left(|A(e_i+e_j)|^4+|A(e_i-e_j)|^4\right).
 \label{eq:Q5}
\end{equation}

Now set $\gamma_a=c a^{-p}$ and first keep $d_a=d>0$ fixed.  Then

\begin{equation}
 w_a=c a^{1-p},\qquad R_a=\frac{c}{d^2}a^{2-p}.
 \label{eq:p-scaling}
\end{equation}

\begin{corollary}[Unique edge-stable, smooth-vanishing window]
The bounded sublevels have a uniform relative edge margin precisely for
$p\ge1$, while the barrier vanishes on every smooth field precisely for
$p<2$.  Thus the only power window with both properties is
\begin{equation}
 \boxed{1\le p<2.}
 \label{eq:window}
\end{equation}
The minimal choice is $p=1$, namely
$\gamma(a)=\bar\gamma/a$, for which $w_a=\bar\gamma$ and a smooth barrier
is $O(a)$.
\end{corollary}

More generally, if $d_a\sim d_0a^\alpha$, the two requirements become

\begin{equation}
 p\ge1,\qquad p+2\alpha<2.
 \label{eq:alpha-window}
\end{equation}

The window is nonempty only for $\alpha<1/2$.  An absolute edge margin also
requires $\alpha=0$.  We therefore retain the fixed value
$\epsilon_a=0.01$ and do not send $\epsilon_a$ either to $1$ or to the
no-zero threshold $-1/3$.

\section{Barrier regimes, the zero Gamma limit, and the no-free-lunch theorem}

Let $P_an$ be the dual-cell piecewise-constant extension of the nodal field
and $I_an$ its tetrahedral affine interpolant.  On the explicitly declared
state space $L^2(\Omega;\RR^4)$ define

\begin{equation}
 \mathfrak B_a(u)=
 \begin{cases}
 \cB_a[n],&u=P_an\text{ for an admissible nodal field},\\
 +\infty,&\text{otherwise}.
 \end{cases}
 \label{eq:embedded-barrier}
\end{equation}

Boundary-node values have zero volume measure, so a zero-energy strong-$L^2$
limit cannot retain a trace unless a coercive base term is also present.

\begin{theorem}[Rigorous barrier regimes]
Fix $d=1-\epsilon>0$ and a periodic shape-regular triangulation family.

\begin{enumerate}[label=(\roman*)]
\item If $R_a\to0$, then in strong $L^2$
\begin{equation}
 \mathfrak B_a\xrightarrow{\Gamma}
 \mathfrak B_0(u):=
 \begin{cases}
 0,&u\in L^2(\Omega;\SSS^3),\\
 +\infty,&\text{otherwise}.
 \end{cases}
 \label{eq:gamma-zero}
\end{equation}
This limit forgets both trace and degree.

\item If $\inf_aR_a>0$, every bounded barrier sublevel gives a uniform
discrete $W^{1,4}$ bound on $I_an$.  The affine fields are precompact in
$C^{0,\beta}$ for every $\beta<1/4$, and normalized-affine degree is closed.

\item If $R_a\to\infty$, the $W^{1,4}$ seminorm tends to zero on a bounded
sublevel.  With the fixed vacuum boundary trace, the only possible limit is
$\ezer$.

\item If $R_a\to R\in(0,\infty)$, Eq.~\eqref{eq:smooth-expansion} identifies
the Cauchy--Born density on fixed smooth sampled fields.  It does not by
itself identify the Gamma limit.  For a periodic multi-cell stencil the
candidate integral density must be obtained from the corresponding
homogenized cell problem; oscillatory correctors may lower the raw
$Q_{\cT}$.  That cell formula is not evaluated here.
\end{enumerate}
\end{theorem}

\begin{proof}
For (i), strong $L^2$ limits of the sphere-valued piecewise-constant fields
remain sphere-valued almost everywhere, giving the $+\infty$ part and the
nonnegative liminf.  Smooth sphere-valued maps which equal the vacuum in a
shrinking boundary collar are dense in $L^2(\Omega;\SSS^3)$.  For each fixed
smooth map, nodal sampling converges strongly and
Eq.~\eqref{eq:smooth-expansion} makes the barrier vanish.  A slow diagonal
choice gives the recovery sequence.

For (ii), Eq.~\eqref{eq:quartic-lower} on the tetrahedral edges and shape
regularity give
\begin{equation}
 \|\nabla I_an\|_{L^4}^4
 \le \frac{C}{R_a}\cB_a[n].
 \label{eq:W14-control}
\end{equation}
Moreover
$\|P_an-I_an\|_{L^4}\le Ca\|\nabla I_an\|_{L^4}$, so both extensions have
the same limit.  Morrey compactness gives the asserted uniform convergence,
which preserves the no-zero interpolation and degree.  If $R_a\to\infty$,
Eq.~\eqref{eq:W14-control} makes the seminorm vanish; the fixed trace and
Poincare's inequality select the vacuum.  Statement (iv) is precisely the
boundary of Eq.~\eqref{eq:smooth-expansion}: periodic discrete-to-continuum
identification requires minimization over cell correctors, not merely
evaluation on the uncorrected affine sample.
\end{proof}

\begin{theorem}[Fixed-$\epsilon$ no-free-lunch theorem]
No scaling of the AP-E8 logarithmic barrier with fixed
$\epsilon\in(-1/3,1)$ makes it both

\begin{enumerate}[label=(\alph*)]
\item vanish on every smooth continuum field, and
\item by itself provide compactness strong enough to close continuum degree
sectors.
\end{enumerate}

At the critical compactness scaling $p=2$, the raw Cauchy--Born consistency
tensors for the six- and five-tetrahedron meshes cannot be made equal by
multiplying one of them by a constant.  Equality or inequivalence of their
homogenized Gamma densities is a separate, unevaluated cell problem.
\end{theorem}

\begin{proof}
Smooth vanishing on every smooth field is equivalent to $R_a\to0$, whereas
the $W^{1,4}$ estimate from the barrier is uniform only when
$\liminf R_a>0$.  Failure of degree closure in the vanishing regime is
explicit.  Choose a smooth map
$U:B_1\to\SSS^3$ of degree one which equals $\ezer$ on a collar of
$\partial B_1$, and put

\[
 n^{(r)}(x)=
 \begin{cases}
 U((x-x_0)/r),&x\in B_r(x_0),\\
 \ezer,&x\notin B_r(x_0).
 \end{cases}
\]

It has degree one and

\[
 \int|\nabla n^{(r)}|^2=O(r),\qquad
 \int|\nabla n^{(r)}|^4=O(r^{-1}).
\]

For a resolved nodal sample, $a/r$ sufficiently small makes every edge
admissible.  Equation~\eqref{eq:phi-bounds} and edge counting in $B_r$
then give $\cB_a[S_an^{(r)}]\le C R_a/r$.  Choose
$r_a=\max\{R_a^{1/2},a^{1/2}\}$.  Then $r_a\to0$,
$r_a/a\to\infty$, and $R_a/r_a\to0$.  The sampled normalized-affine maps
therefore have degree one and bounded, indeed vanishing, barrier energy,
but converge strongly in $L^2$ to the degree-zero vacuum.  Thus a vanishing
barrier cannot close degree sectors.

For the final assertion, take a linear gradient with
$Ae_1=v$, $Ae_2=Ae_3=0$.  Equations~\eqref{eq:Q6}--\eqref{eq:Q5} give
$Q_{6,+}=4|v|^4$ and $Q_5=3|v|^4$.  If a scalar rescaling matched these,
it would use a factor $4/3$.  Instead take
$Ae_1=Ae_2=v$, $Ae_3=0$; then $Q_{6,+}=36|v|^4$ and
$Q_5=12|v|^4$, whose ratio is $3$.  Hence the two uncorrected smooth-sampling
quartics are not proportional.
\end{proof}

\begin{remark}[What the no-go does not prove]
The degree-one bubble has base Skyrme energy of order $1/r$.  Consequently
the preceding construction concerns the barrier alone and does not prove
that bounded sublevels of the \emph{complete} Skyrme action lose degree.
Whether the base Skyrme minors themselves supply topological-current
compactness is exactly the remaining theorem-level blocker.
\end{remark}

\section{Conditional Gamma theorem for the complete action}

\begin{theorem}[Stable addition of a vanishing barrier]
Assume that the AP-E7 base functionals $E_a$ satisfy, in strong
$L^2\times L^2$,

\begin{enumerate}[label=(\roman*)]
\item $E_a\xrightarrow{\Gamma}E_0$;
\item their sublevels are equicoercive;
\item for every $u=(n,s)$ with $E_0(u)<\infty$, there are smooth pairs
$u^k=(n^k,s^k)$, with the declared boundary data, such that
\begin{equation}
 u^k\to u\text{ in }L^2\times L^2,\qquad E_0(u^k)\to E_0(u);
 \label{eq:smooth-density}
\end{equation}
\item for every fixed $k$, the nodal samples $S_au^k$ recover the base
energy:
\begin{equation}
 S_au^k\to u^k,\qquad E_a(S_au^k)\to E_0(u^k).
 \label{eq:fixed-smooth-recovery}
\end{equation}
\end{enumerate}

If
\begin{equation}
 \frac{a^2}{d_a}\longrightarrow0,
 \qquad
 R_a=\frac{\gamma_a a^2}{d_a^2}\longrightarrow0,
 \label{eq:conditional-hypotheses}
\end{equation}
then
\begin{equation}
 E_a+\cB_a\xrightarrow{\Gamma}E_0.
 \label{eq:conditional-gamma}
\end{equation}
The full family inherits $L^2\times L^2$ equicoercivity from $E_a$.
\end{theorem}

\begin{proof}
The liminf follows from $\cB_a\ge0$.  For every fixed $k$,
Eq.~\eqref{eq:smooth-expansion} and
Eq.~\eqref{eq:conditional-hypotheses} give
$\cB_a[S_an^k]\to0$; the constants hidden in the expansion may depend on
$k$ but not on $a$.  First take $a\to0$ at fixed $k$, then choose a slow
diagonal $k=k(a)\to\infty$.  Equations~\eqref{eq:smooth-density} and
\eqref{eq:fixed-smooth-recovery} give the required full recovery sequence.
Finally,
$E_a\le E_a+\cB_a$, so every full-action sublevel lies in the corresponding
equicoercive base sublevel.
\end{proof}

This theorem is unconditional as an abstract stability statement, but its
four hypotheses have not yet been proved for the specific one-corner forward
Skyrme discretization.  The missing statements are:

\begin{enumerate}
\item a discrete compensated-compactness and liminf theorem for the three
forward Skyrme minors;
\item smooth fixed-boundary, fixed-degree density in the natural class
\[
 \{n\in W^{1,2}:\partial_i n\wedge\partial_j n\in L^2\};
\]
\item exclusion or accounting of a topological-current concentration defect;
\item translation tightness when $L\to\infty$.
\end{enumerate}

Without centering or quotienting translations, joint $a\downarrow0$,
$L\uparrow\infty$ equicoercivity is false: a localized soliton can translate
to infinity while retaining its energy and norm.

\section{Alternative triangulations and translated starts}

The numerical card uses exactly the same tetrahedral complex for its barrier
edges and its normalized-affine degree.  It tests:

\begin{enumerate}
\item the original uniform six-tetrahedron Freudenthal mesh;
\item both phases of the conforming checkerboard five-tetrahedron mesh, whose
central parity is $\mathrm{phase}+i+j+k\pmod2$;
\item starts translated by noninteger lattice offsets before imposing the
exact vacuum boundary;
\item wider fixed-$L$ spacing and fixed-$a$ volume sequences;
\item the matched trajectories $p=0,1,2$, normalized so that
$\gamma(0.4)=1$.
\end{enumerate}

The five-tetrahedron mesh has one central tetrahedron of determinant magnitude
two and four corner tetrahedra of determinant magnitude one in every cube.
The checkerboard parity flip makes every shared face diagonal agree.  Exact
combinatorial tests check nonzero volume, spatial orientation, face
multiplicity, Euler characteristic one, and degree on regular targets.

For each relaxed background, the card records total, base, and barrier
energies; direct tangent-plus-scalar stationarity; minimum edge dot; degree at
three generic regular targets; the $1-n_0$ barycentre and centered radius;
an absolute-baryon-density proxy radius; and high-quantile local gradient
concentration.  A translated start is therefore not silently recentered in
the reported observables.

\section{Numerical verdict}

The production values in this section are generated by

\begin{center}
\path{route_f/code/scan_ap_e9_gamma_triangulation.py}.
\end{center}

The machine-readable and human-readable cards are

\begin{center}
\path{route_f/output/ap_e9_gamma_triangulation.json},\qquad
\path{route_f/output/ap_e9_gamma_triangulation.md}.
\end{center}

All $23$ independently relaxed cases are stationary within the declared
$2\times10^{-6}$ projected-gradient-density tolerance, remain admissible,
and return degree $(1,1,1)$ at the three regular targets.  The largest
gradient density is $1.7224\times10^{-6}$ and the smallest pair margin is
$0.067786$.  The smooth compact-support test gives

\begin{center}
\begin{tabular}{rrrr}
\toprule
$p$&fitted barrier slope&predicted $2-p$&$R^2$\\
\midrule
0&2.159102&2&0.999141\\
1&1.159102&1&0.997025\\
2&0.159102&0&0.863298\\
\bottomrule
\end{tabular}
\end{center}

Thus the fixed-profile calculation detects the predicted smooth-sampling
exponent split.  It
does not imply that a relaxed branch has entered that asymptotic regime.
For the matched $p=1$, fixed-$L=6$ branch the production sequence is

\begin{center}
\small
\begin{tabular}{rrrrrr}
\toprule
$a$&$E_a$&$\cB_a$&$\cF_a$&centered RMS&gradient density\\
\midrule
0.428571&55.307957&18.487241&73.795198&1.298396&$2.36\times10^{-7}$\\
0.375000&55.677145&17.909776&73.586921&1.261284&$1.94\times10^{-7}$\\
0.333333&56.448068&17.495634&73.943702&1.232911&$1.08\times10^{-6}$\\
0.300000&57.507365&17.148880&74.656246&1.211449&$2.28\times10^{-7}$\\
0.272727&58.801673&16.793372&75.595045&1.196040&$3.21\times10^{-7}$\\
0.250000&60.320889&16.351169&76.672058&1.186597&$5.16\times10^{-7}$\\
\bottomrule
\end{tabular}
\end{center}

The finest-three total-energy and radius spreads are $2.629\%$ and
$2.051\%$, respectively, but the fitted barrier slope is only $0.2196$,
outside the predeclared $1.0\pm0.4$ window.  Hence the relaxed fields have
not demonstrated the predicted $O(a)$ barrier disappearance.

At fixed $a=0.4$, increasing the box gives

\begin{center}
\begin{tabular}{rrrrr}
\toprule
$L$&$N$&$\cF_a$&centered RMS&pair margin\\
\midrule
6&16&73.627393&1.274459&0.080722\\
8&21&73.346860&1.425707&0.085418\\
10&26&73.289479&1.510286&0.085975\\
12&31&73.273437&1.558499&0.086231\\
\bottomrule
\end{tabular}
\end{center}

The largest-three energy spread is only $0.1001\%$, whereas the radius
spread is $8.521\%$, exceeding its $5\%$ gate.  Energy stabilization alone
therefore does not establish volume stabilization.

The alternative-mesh screen was repeated at two spacings, with both
centered and translated starts:

\begin{center}
\small
\begin{tabular}{llrrrr}
\toprule
$a$&mesh&centered $\cF_a$&translated $\cF_a$&centered RMS&pair margin\\
\midrule
0.4&six-tet&73.627393&73.614920&1.274459&0.080722\\
0.4&five-tet phase 0&69.630225&69.630225&1.210207&0.085973\\
0.4&five-tet phase 1&69.620878&69.620878&1.212765&0.086169\\
0.3&six-tet&74.656246&74.656246&1.211449&0.109410\\
0.3&five-tet phase 0&70.659350&70.659350&1.128126&0.100946\\
0.3&five-tet phase 1&70.658169&70.658169&1.128277&0.101019\\
\bottomrule
\end{tabular}
\end{center}

Translation changes the terminal energy negligibly, but six-versus-five-tet
energy spreads remain $5.442\%$ at $a=0.4$ and $5.355\%$ at $a=0.3$,
above the $3\%$ gate.  They are not visibly shrinking.  On the common
$N=21,L=6$ grid, the two smooth-vanishing controls $p=0$ and $p=1$ give
$\cF_a=69.844123$ and $74.656246$: their $6.446\%$ spread also exceeds
the $3\%$ regulator gate, although their radius spread $3.897\%$ passes.

Consequently the strict card passes all eight implementation and provenance
checks but returns

\[
 \boxed{\texttt{numerical\_regulator\_stability=false},\qquad
        \texttt{continuum\_background=false}.}
\]

The failure is informative rather than an optimizer failure: every required
stationary, admissibility, and degree check passes, while four independent
continuum diagnostics fail.  Irrespective of that empirical verdict, a
finite collection of convergent observables could not replace the missing
Skyrme-minor liminf and topological-current compactness proof.

\section{Recent literature and exact transfer boundary}

No located paper proves the three-dimensional $\SSS^3$-valued AP-E8
functional with its logarithmic edge barrier.  The closest recent rigorous
work proves charge-measure compactness and Gamma convergence for a two-
dimensional $\SSS^2$ baby-Skyrme setting
\cite{BrianiCicaleseKreutz2026}; it is a proof architecture, not a theorem
that transfers dimensions and targets.  Recent sphere-valued finite-element
and triangulation analyses identify the need for shape regularity,
consistent weights, and stability hypotheses
\cite{BartelsBoehnleinPalusSander2025,GasterLoustauMonsaingeon2023,
BartelsPalusWang2023}.  Scaling thresholds can change Gamma limits in other
spin systems \cite{CicaleseReggianiSolombrino2024}, but that result does not
contain this barrier.

The checkerboard five-tetrahedron construction and the warning that a lattice
cutoff can be part of the model have a direct three-dimensional predecessor
\cite{SchrammSvetitsky2000}.  Earlier geometric degree and admissibility ideas
\cite{BergLuescher1981,Luescher1982} motivate the design but do not imply a
continuum theorem here.  Three-dimensional lattice Skyrmion branches are
known to be numerically sensitive near continuum regimes
\cite{CharalampidisIoannidouKevrekidis2015}, which is why translated starts
and branch diagnostics are mandatory rather than cosmetic.

\section{Fail-closed decision and ordered continuation}

\begin{gate}[Hessian authorization]
The full same-action Riemann Hessian and regulated determinant variation may
start only after all of the following are true:

\begin{enumerate}
\item one $p<2$ background sequence is stationary and stable under spacing,
volume, triangulation, translation, and regulator changes;
\item the barrier fraction vanishes with the predicted scaling;
\item the base Skyrme-minor liminf and fixed-degree recovery problem is
closed, or an explicitly modified continuum action is adopted;
\item translation tightness is fixed by a declared quotient or a physical
centering condition, not by an optimization anchor.
\end{enumerate}
\end{gate}

Until then:

\begin{align*}
 \texttt{regulator\_stable\_continuum\_background}&=\texttt{false},\\
 \texttt{same\_action\_hessian\_authorized}&=\texttt{false}.
\end{align*}

and the degree-one Route-E portal remains prohibited.  The finite
GW/domain-wall kernel and the actual $SO(3)$ mapping-torus mod-two index
remain parallel lanes.  The mathematically preferred next choices are:

\begin{enumerate}
\item prove compactness of the discrete Skyrme topological current in the
natural minor-bounded class;
\item evaluate the periodic finite-$R$ homogenized cell problem before
identifying any raw $Q_{\cT}$ with a Gamma density;
\item if the base-minor route fails, adopt the critical $p=2$ term as a declared physical
quartic and replace the raw stencil by a rotationally calibrated,
triangulation-independent discretization;
\item continue the $p=1$, fixed-$\epsilon$ numerical sequence only as a
vanishing-regulator candidate, never as a proof of degree closure.
\end{enumerate}

\bibliographystyle{unsrt}
\bibliography{route_f/tex/ap_e9_gamma_limit_regulator}

\end{document}
