\section{AP-E12: endpoint graph density and relaxed-minimizer audit}

AP-E12 makes the AP-E11 regularity gate precise.  For fixed vacuum trace,
define
\begin{equation}
 \mathcal G_B^2=\{u\in W^{1,2}(\Omega;S^3):
 M_2(Du),M_3(Du)\in L^2,\ \deg u=B\}
 \label{eq:e12-graph}
\end{equation}
with strong $L^2$ convergence of $u$, $Du$, $M_2(Du)$, and $M_3(Du)$.
Graph convergence already closes degree: if $u_j,u$ are sphere-valued, then
\begin{equation}
 2\pi^2|B(u_j)-B(u)|\leq
 \|u_j-u\|_2\|M_3(Du_j)\|_2
 +|\Omega|^{1/2}\|M_3(Du_j)-M_3(Du)\|_2.
 \label{eq:e12-degree-continuity}
\end{equation}
Therefore a target-valued graph-dense smooth sequence is automatically in the
same integer degree for all sufficiently large indices.  The missing theorem
is target-valued endpoint graph density, not a separate degree repair.

For the AP-E11 continuum density
\begin{equation}
 W(F)=\frac12\{|F|^2+R|M_2(F)|^2+K|M_3(F)|^2\},
 \label{eq:e12-density}
\end{equation}
every minor of $F+t(a\otimes\xi)$ is affine in $t$.  Hence
\begin{equation}
 D^2W(F)[a\otimes\xi,a\otimes\xi]
 =|a|^2|\xi|^2+R|DM_2(F)[a\otimes\xi]|^2
 +K|DM_3(F)[a\otimes\xi]|^2,
 \label{eq:e12-lh}
\end{equation}
so the uniform Legendre--Hadamard constant is one.  More strongly, periodic
null-Lagrangian means give the exact identity
\begin{align}
 \int\{W(F+D\varphi)-W(F)\}
 =\frac12\int\{&|D\varphi|^2
 +R|M_2(F+D\varphi)-M_2(F)|^2\notag\\
 &+K|M_3(F+D\varphi)-M_3(F)|^2\}.
 \label{eq:e12-strong-qc}
\end{align}
This proves model-specific strong quasiconvexity but does not construct the
trace-preserving $S^3$ recovery sequence.

The classical Cartesian approximation result is exponent-losing:
$\operatorname{Cart}^{\bm p}$ is strongly approximable in every
$\mathcal A^{\bm q}$ with $\bm q<\bm p$, not at the endpoint
\cite{Maly1991}.  Area approximation controls all minors in $L^1$
\cite{Mucci2001}.  A scale-sharp audit also shows why the direct Mal\'y
two-hole dipole does not provide the missing counterexample here.  For
$u(r,\theta,z)=r^\alpha\gamma(\theta)$,
\begin{equation}
 \int|M_2(Du)|^2\sim\int r^{4\alpha-3}\,dr<\infty
 \quad\Longleftrightarrow\quad\alpha>\frac12,
 \label{eq:e12-dipole-energy}
\end{equation}
whereas Cauchy--Schwarz forces every core filling to pay at least
$c r^{4\alpha-2}$; a non-vanishing cost requires $\alpha\leq1/2$.  For
$r^{1/2}\log(e/r)^{-\beta}$, minor integrability requires $\beta>1/4$
while the filling bound tends to zero.  This excludes that mechanism, not
all possible endpoint concentrations.

The fallback cannot presently be closed by importing generic regularity.
The formal stress and classical equation are
\begin{align}
 P(F)&=F+R\{(\operatorname{tr}G)F-FG\}+KF\operatorname{cof}G,
 \qquad G=F^TF,\label{eq:e12-stress}\\
 (I-u\otimes u)&\{-\operatorname{div}P(Du)-m^2e_0\}=0.
 \label{eq:e12-el}
\end{align}
A relaxed minimizer is not authorized to satisfy \eqref{eq:e12-el} until a
local fixed-trace recovery theorem is supplied.  Moreover
$W(F)\lesssim1+|F|^6$ with $(n,p,q)=(3,2,6)$, while the 2024 smooth partial-
regularity theorem for relaxed strongly quasiconvex integrands requires
$q<\min\{np/(n-1),p+1\}=3$ \cite{GmeinederKristensen2024}.  It also does not
include the $S^3$ constraint and degree relaxation.

The production card passes $9/9$.  Three successively finer backgrounds have
maximum one-tetrahedron energy fractions
$3.966\times10^{-3}$, $1.849\times10^{-3}$, and
$1.173\times10^{-3}$.  Three amplitude-$0.24$ tangent perturbations re-relax
to energy spread $3.38\times10^{-11}$, maximum radial-CDF distance
$5.70\times10^{-7}$, and field RMS $1.31\times10^{-5}$ after quotienting
integer translations and proper target $SO(3)$.  This is finite-dimensional
same-basin evidence only, not continuum isolation.  The authorization is
\begin{equation}
 \boxed{\begin{gathered}
 C_{\rm graph\ degree}=C_{\rm strong\ QC}=C_{\rm dipole\ no\mbox{-}go}
 =\mathrm{true},\\
 C_{\rm endpoint\ density}=\mathrm{false\ (not\ disproved)},\\
 C_{\rm weak\ EL}=C_{\rm partial\ regularity}=C_{\rm classicality}
 =C_{\rm isolation}=C_{\rm Hessian}=C_{\det}=\mathrm{false}.
 \end{gathered}}
 \label{eq:e12-decision}
\end{equation}
The next theorem must be an annular target-valued endpoint replacement with
equiintegrable complete minors, or a reverse-H\"older estimate giving local
$L^{2+\delta}$ control of the complete-minor vector followed by a controlled
$S^3$ projection.  No same-action Riemann Hessian is assembled before one of
those paths also establishes classicality and continuum isolation.
