\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}

\newcommand{\SU}{\mathrm{SU}}
\newcommand{\Spin}{\mathrm{Spin}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Res}{\mathrm{Res}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\bml}{B-L}
\newcommand{\uc}{u^c}
\newcommand{\dc}{d^c}
\newcommand{\nuc}{\nu^c}
\newcommand{\ec}{e^c}

\title{Route C Bootstrap Derivation Ledger through P12-S}
\author{BoYu Chen}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This note records the derivations generated in Route C stages P1--P12-S.
It is a derivation ledger, not a claim that on-shell consistency has already
derived a complete GUT.  The current Route C program uses the one-family
Standard Model spectrum with a right-handed neutrino as baseline, builds
charge-filtered symbolic four-point pole components, checks conditional
residue factorization/positivity, marks Ward-identity completion requirements,
compares anomaly/chiral consistency across $\SU(5)$, Pati--Salam,
$\Spin(10)$, $E_6$, and superstring-derived completions, and classifies
controlled high-energy-growth and low-energy proton-bound readiness
requirements, and closes the first pass with a comparative theory scorecard.
P9 then locks the branch to $\Spin(10)$ and supplies the first sparse
action-completion ledger for the half-spinor broken-generator maps and the
remaining Goldstone/Higgs, mediator, flavor, and proton-bound inputs.
P10 chooses a staged source branch and converts the symbolic vector masses into
a diagonalizable mass matrix with one hypercharge zero mode.
P11 replays the P6/P7 matching gates with those staged masses and separates
adjoint current-vector matching from scalar/source chiral-pair mass debt.
P12-S records both post-P11 directions, activates the scalar/source
chiral-pair branch first, and assigns symbolic scalar/source mass denominators
to all P7 chiral-pair rows while leaving physical proton bounds conditional.
\end{abstract}

\section{Boundary of the Ledger}

Route C tests whether
\begin{equation}
\begin{split}
  &\text{Lorentz}
  + \text{unitarity}
  + \text{factorization}
  + \text{Ward identities} \\
  &\qquad
  + \text{anomaly cancellation}
  + \text{controlled high-energy behavior}
\end{split}
\end{equation}
can filter conditional GUT branches.  It must not be read as
\begin{equation}
  \text{four axioms} \Longrightarrow \text{the full GUT}.
\end{equation}
The honest statement is instead
\begin{equation}
  \text{on-shell consistency} \Longrightarrow
  \text{filters on allowed action-level GUT branches}.
\end{equation}

The baseline external spectrum is one left-handed family plus a
right-handed-neutrino conjugate field,
\begin{equation}
  \mathcal F_{\rm SM+\nu^c}
  =
  Q \oplus L \oplus \uc \oplus \dc \oplus \nuc \oplus \ec .
\end{equation}
All fields are written as left-handed Weyl fields.

\section{P1: External-State Charges and Anomalies}

\subsection{Charge Table}

The P1 charge ledger fixes the Standard Model face conventions shown in
Table~\ref{tab:p1-charges}.

\begin{table}[h]
\centering
\begin{tabular}{c c c c c c}
\toprule
state & $\SU(3)_C$ & $\SU(2)_L$ & $Y$ & $\bml$ & multiplicity \\
\midrule
$Q$    & $3$        & $2$ & $1/6$   & $1/3$  & $6$ \\
$L$    & $1$        & $2$ & $-1/2$  & $-1$   & $2$ \\
$\uc$  & $\bar 3$   & $1$ & $-2/3$  & $-1/3$ & $3$ \\
$\dc$  & $\bar 3$   & $1$ & $1/3$   & $-1/3$ & $3$ \\
$\nuc$ & $1$        & $1$ & $0$     & $1$    & $1$ \\
$\ec$  & $1$        & $1$ & $1$     & $1$    & $1$ \\
\bottomrule
\end{tabular}
\caption{P1 baseline spectrum.  The fields $\uc,\dc,\nuc,\ec$ are
left-handed conjugate Weyl fields, so the listed charges are the charges
of those conjugate fields.}
\label{tab:p1-charges}
\end{table}

\subsection{Hypercharge Normalization}

For one full family plus $\nuc$, the hypercharge trace is
\begin{align}
  \Tr Y^2
  &=
  6\left(\frac{1}{6}\right)^2
  +2\left(-\frac{1}{2}\right)^2
  +3\left(-\frac{2}{3}\right)^2
  +3\left(\frac{1}{3}\right)^2
  +1\cdot 0^2
  +1\cdot 1^2                                              \notag\\
  &=\frac{10}{3}.
\end{align}
With $\Tr_{\mathbf 2}T_{3L}^2=1/2$, the weak trace is
\begin{equation}
  \Tr T_{3L}^2
  =
  3\cdot \frac{1}{2}
  +1\cdot \frac{1}{2}
  =2.
\end{equation}
Therefore
\begin{equation}
  \frac{\Tr Y^2}{\Tr T_{3L}^2}=\frac{5}{3},
\end{equation}
which is the standard GUT hypercharge normalization.

\subsection{Perturbative and Global Anomaly Checks}

With the conventions of Table~\ref{tab:p1-charges}, the exact rational
ledger verifies
\begin{equation}
  \mathcal A_{\SU(3)^3}
  =
  2A(3)+A(\bar 3)+A(\bar 3)
  =
  2-1-1=0 .
\end{equation}
The mixed color-hypercharge anomaly is
\begin{equation}
  \mathcal A_{\SU(3)^2U(1)_Y}
  =
  2T(3)\frac{1}{6}
  +T(\bar 3)\left(-\frac{2}{3}\right)
  +T(\bar 3)\frac{1}{3}
  =
  \frac{1}{6}-\frac{1}{3}+\frac{1}{6}=0,
\end{equation}
where $T(3)=T(\bar 3)=1/2$.  The weak-hypercharge anomaly is
\begin{equation}
  \mathcal A_{\SU(2)^2U(1)_Y}
  =
  3T(2)\frac{1}{6}
  +T(2)\left(-\frac{1}{2}\right)
  =
  \frac{1}{4}-\frac{1}{4}=0.
\end{equation}
The gravitational and cubic hypercharge anomalies are
\begin{align}
  \mathcal A_{\mathrm{grav}^2U(1)_Y}
  &=
  6\frac{1}{6}
  +2\left(-\frac{1}{2}\right)
  +3\left(-\frac{2}{3}\right)
  +3\frac{1}{3}
  +0+1
  =0,                                                        \\
  \mathcal A_{U(1)_Y^3}
  &=
  6\left(\frac{1}{6}\right)^3
  +2\left(-\frac{1}{2}\right)^3
  +3\left(-\frac{2}{3}\right)^3
  +3\left(\frac{1}{3}\right)^3
  +0^3+1^3
  =0.
\end{align}
The same exact ledger verifies the analogous $\bml$ and mixed
$Y$--$\bml$ anomalies,
\begin{equation}
  \SU(3)^2(\bml),\quad
  \SU(2)^2(\bml),\quad
  \mathrm{grav}^2(\bml),\quad
  (\bml)^3,\quad
  Y^2(\bml),\quad
  Y(\bml)^2,
\end{equation}
all vanish.  The Witten $\SU(2)$ check passes because one family contains
three $Q$ doublets and one $L$ doublet, hence four left-handed doublets.

\section{P2: Symbolic Four-Point Pole Ansatz}

The first pole ansatz is an all-incoming chiral-bilinear seed,
\begin{equation}
  \mathcal A_4(12|34)
  =
  \sum_X\frac{R_s(X)}{s-M_X^2}+C_6(12|34),
  \qquad
  R_s(X)=g_{12X}g_{34\bar X}.
\end{equation}
P2 does not declare the mediator spectrum.  It only computes which
symbolic pole components are not forbidden by the P1 charges and by
non-Abelian conjugacy of pair products.

The generated P2 ledger gives the numerical summary
\begin{equation}
\begin{array}{c|c}
\text{quantity} & \text{value} \\
\hline
\text{pair types} & 21\\
\text{pair-product components} & 31\\
\text{tested pair-component pairings} & 496\\
\text{allowed symbolic pole components} & 18\\
\text{forbidden by Abelian charge} & 455\\
\text{forbidden after Abelian pass by non-Abelian conjugacy} & 23
\end{array}
\end{equation}
The proton-operator seeds retained at this purely symbolic level are
\begin{equation}
  QQQL:\ 2 \ \text{allowed pole components},\qquad
  \uc\uc\dc\ec:\ 2 \ \text{allowed pole components}.
\end{equation}
The entries
\begin{equation}
  QQ\uc\ec,\qquad QL\uc\dc
\end{equation}
have zero allowed pole components in this first all-incoming symbolic
seed.  These zeros are not no-go theorems for full models; they are
bookkeeping results for the declared P2 ansatz and charge conventions.

\section{P3: Residue Factorization and Positivity}

For a declared mediator sector $X$, let $\alpha$ label all two-particle
channels that can couple to $X$.  Near a positive-norm simple pole,
tree-level factorization requires
\begin{equation}
  \Res_X \mathcal A_{\alpha\beta}
  =
  g_{\alpha X}g_{\beta X}^\ast .
\end{equation}
Thus the residue matrix is a Gram matrix,
\begin{equation}
  R_X = g_X g_X^\dagger,
\end{equation}
and is positive semidefinite in a positive-metric Hilbert space:
\begin{equation}
  v^\dagger R_X v = |g_X^\dagger v|^2\ge 0.
\end{equation}
A wrong-sign mediator metric reverses the sign and fails the unit-coupling
stress test.

The P3 machine ledger checks the P2-allowed poles and reports
\begin{equation}
\begin{array}{c|c}
\text{quantity} & \text{value} \\
\hline
\text{mediator sectors} & 26\\
\text{total vertex channels} & 31\\
\text{P2 allowed poles checked} & 18\\
\text{factorization checks passed} & 18\\
\text{PSD blocks under positive metric} & 26\\
\text{largest channel-block size} & 3
\end{array}
\end{equation}
For a unit-coupling block with $n$ channels, the stress spectrum is
\begin{equation}
  \mathrm{spec}(R_X)=\{n,0,\ldots,0\},
  \qquad
  \mathrm{spec}(-R_X)=\{-n,0,\ldots,0\},
\end{equation}
which is the numerical pattern seen in the P3 output.

\section{P4: Ward-Identity Bookkeeping}

For an unbroken massless gauge boson, the target Ward check is
\begin{equation}
  \epsilon_\mu\rightarrow p_\mu,\qquad p_\mu\mathcal M^\mu=0.
\end{equation}
For a broken massive vector, the target relation is the generalized
Ward/Slavnov--Taylor form
\begin{equation}
  p_\mu\mathcal M^\mu(V_X)=M_X\mathcal M(\phi_X),
\end{equation}
so a Goldstone/Higgs/source completion is required before a true Ward
identity proof can be claimed.

The P4 ledger separates unbroken SM currents from broken/off-face
currents:
\begin{equation}
\begin{array}{c|c}
\text{quantity} & \text{value} \\
\hline
\text{unbroken SM current sectors} & 3\\
\text{current transitions checked} & 36\\
\text{massless diagonal transitions ready} & 6\\
\text{broken/off-face transitions needing completion} & 30\\
\text{mediator sectors inspected} & 26\\
\text{mediator sectors needing completion if vector} & 26
\end{array}
\end{equation}
The bookkeeping-ready unbroken sectors are
\begin{equation}
  \SU(3)_C,\qquad \SU(2)_L,\qquad U(1)_Y.
\end{equation}
All off-face $\Spin(10)$, Pati--Salam leptoquark, and $\SU(2)_R$
charged-current transitions are flagged as needing explicit generator
matrices, massive-vector data, and Goldstone/Higgs/source completion.

\section{P5: Anomaly and Chiral-Consistency Candidate Ledger}

P5 compares candidate branches against the P1 baseline.  The structural
filter used for the minimal Route C field-theory comparison is
\begin{equation}
\begin{split}
  &\text{simple group}
  +\text{one irreducible family object}
  +\text{contains }\nuc  \\
  &\qquad
  +\text{no chiral SM exotics}
  +\text{minimal standard realization}.
\end{split}
\end{equation}

\subsection{SU(5)}

One family plus $\nuc$ is realized as
\begin{equation}
  10\oplus \bar 5\oplus 1.
\end{equation}
The cubic anomaly cancels:
\begin{equation}
  A(10)+A(\bar 5)+A(1)=1-1+0=0.
\end{equation}
Also $\pi_4(\SU(5))=0$ in the standard four-dimensional global-anomaly
check.  However, the family is not one irreducible object; therefore
$\SU(5)$ is anomaly-consistent but fails the single-object filter.

\subsection{Pati--Salam}

The standard Pati--Salam family is
\begin{equation}
  (4,2,1)\oplus(\bar 4,1,2)
  \quad\text{under}\quad
  \SU(4)_C\times\SU(2)_L\times\SU(2)_R .
\end{equation}
The $\SU(4)_C^3$ anomaly cancels because
\begin{equation}
  2A(4)+2A(\bar 4)=2-2=0.
\end{equation}
The Witten checks pass because $\dim(4)=4$ gives four $\SU(2)_L$
doublets and four $\SU(2)_R$ doublets.  Pati--Salam is physically natural
and anomaly-consistent, but it is a product group and not a single
irreducible family object under a simple group.

\subsection{Spin(10)}

The standard $\Spin(10)$ family is the half-spinor
\begin{equation}
  16.
\end{equation}
It contains the full
\begin{equation}
  Q\oplus L\oplus\uc\oplus\dc\oplus\nuc\oplus\ec
\end{equation}
after restriction to the Standard Model face.  The $D_5$ algebra has no
independent cubic gauge-anomaly invariant in this standard check, and
$\pi_4(\Spin(10))=0$.  Therefore $\Spin(10):16$ is anomaly-safe and is the
standard minimal single-object survivor under the stated Route C
pre-filter.

\subsection{E6}

The $E_6$ fundamental representation restricts as
\begin{equation}
  27\longrightarrow 16\oplus 10\oplus 1
  \qquad \text{under } \Spin(10).
\end{equation}
It contains a $\Spin(10)$ family, but also contains extra $10\oplus 1$
states.  Since $E_6$ has no independent cubic gauge-anomaly invariant for
the standard $27$, the anomaly status is acceptable, but the branch
requires an explicit lifting/vectorlike audit for the extra states.  It is
therefore not the minimal Route C survivor.

\subsection{Superstring-Derived Completions}

Superstring-derived completions are not a single four-dimensional
field-theory group.  They form a UV-completion class.  A string-derived
branch must supply compactification-specific data:
\begin{equation}
  \text{Green--Schwarz/tadpole/modular consistency},
  \qquad
  \text{massless spectrum},
  \qquad
  \text{chiral index},
\end{equation}
together with exotics lifting and matching to the Route-A
representation/index skeleton.  Such branches may provide stronger
high-energy softness or tower structure, but P5 does not treat them as a
single fixed four-dimensional candidate.

\subsection{P5 Numerical Summary}

The generated P5 ledger reports
\begin{equation}
\begin{array}{c|c}
\text{quantity} & \text{value}\\
\hline
\text{candidates inspected} & 5\\
\text{field-theory candidates} & 4\\
\text{UV-completion classes} & 1\\
\text{P1 baseline anomalies pass} & \text{true}\\
\text{minimal single-object survivor} & \Spin(10)
\end{array}
\end{equation}
This result should be read narrowly: passing anomaly checks alone does not
select a GUT.  The selection of $\Spin(10)$ occurs only after imposing the
Route C minimal single-object family filter.

\section{P6: Controlled High-Energy-Growth Audit}

P6 consumes the P3 residue blocks and the P4 Ward-completion ledger.  Its
purpose is not to compute a full four-point amplitude.  Its purpose is to
classify which symbolic branches would have uncontrolled high-energy growth
if treated as isolated finite broken-vector exchange.

For a finite massive vector, the dangerous contribution is the longitudinal
propagator term.  A conservative schematic form is
\begin{equation}
  \mathcal A_L
  \sim
  \frac{(J\cdot p)(J'\cdot p)}{M_X^2(s-M_X^2)}.
\end{equation}
If the broken current is not completed by the corresponding Goldstone/Higgs
sector, this can scale as
\begin{equation}
  \mathcal A_L \sim \frac{s}{M_X^2}
  \quad\text{or worse}
\end{equation}
in the high-energy regime.  Therefore the required broken-vector target is
again the generalized Ward/Slavnov--Taylor identity
\begin{equation}
  p_\mu\mathcal M^\mu(V_X)=M_X\mathcal M(\phi_X).
\end{equation}

The generated P6 ledger reports
\begin{equation}
\begin{array}{c|c}
\text{quantity} & \text{value}\\
\hline
\text{mediator sectors inspected} & 26\\
\text{finite-vector branches needing completion} & 26\\
\text{unbroken-vector branches bookkeeping-ready} & 0\\
\text{scalar/auxiliary branches without longitudinal-vector risk} & 26\\
\text{contact-only components needing UV completion} & 18\\
\text{broken transitions needing completion} & 30\\
\text{tower-like UV forced now} & \text{false}
\end{array}
\end{equation}
Thus every current P3 mediator sector, if interpreted as a finite broken
vector, needs explicit finite-completion data:
\begin{equation}
  \{\text{broken generator},\ M_X,\ \phi_X,\ \text{Higgs/source sector},
  \ \text{symmetry-fixed contact/numerator terms}\}.
\end{equation}

If a symbolic mediator is instead interpreted as scalar or auxiliary
exchange, the longitudinal-vector Ward problem is absent.  This is only a
bookkeeping statement; spin-statistics, action existence, low-energy
matching, and perturbative unitarity remain separate checks.

A contact-only four-fermion EFT normalization generically scales like
\begin{equation}
  \mathcal A_{\rm contact}\sim \frac{s}{\Lambda^2},
\end{equation}
so contact terms may encode low-energy matching but cannot by themselves
serve as high-energy softness proofs.

Finally, P6 does not force a string or tower completion.  It states the
conditional comparison rule:
\begin{equation}
\begin{split}
  \text{finite Goldstone/Higgs/source completion fails}
  \quad\Longrightarrow\quad\\
  \text{tower-like UV completion becomes a serious comparison class}.
\end{split}
\end{equation}
Superstring-derived completions therefore remain comparison branches, not
P6 conclusions.

\section{P7: Low-Energy Matching and Proton-Bound Readiness}

P7 converts the P2/P3 symbolic pole data into conditional low-energy
dimension-six matching rows.  It respects the P6 gate: a vector interpretation
of a broken mediator cannot be promoted to a physical Wilson coefficient until
the finite Goldstone/Higgs/source completion has been supplied.

For a symbolic pole with mediator $X$, P7 records the matching template
\begin{equation}
  C_6[\mathcal O;X]
  =
  \frac{g_{\mathrm{left},X}g_{\mathrm{right},X}^\ast}{M_X^2}.
\end{equation}
This is only a gauge-basis symbolic coefficient.  It is not yet a physical
proton-decay Wilson coefficient.

Using the left-handed Weyl charge convention, the global bookkeeping assigns
\begin{equation}
  B(Q)=\frac13,\quad B(\uc)=B(\dc)=-\frac13,\quad
  L(L)=1,\quad L(\nuc)=L(\ec)=-1.
\end{equation}
The generated P7 ledger reports
\begin{equation}
\begin{array}{c|c}
\text{quantity} & \text{value}\\
\hline
\text{allowed symbolic poles processed} & 18\\
\text{B and L conserving poles} & 12\\
\text{standard BNV seed poles} & 4\\
\text{BNV-with-sterile-neutrino poles} & 2\\
\text{baryon-violating symbolic poles} & 6\\
\text{BNV vector poles blocked by P6 completion} & 6\\
\text{physical proton bounds evaluable now} & 0\\
\text{all physical bounds conditional} & \text{true}
\end{array}
\end{equation}

The standard baryon-violating seeds include
\begin{equation}
  QQQL,\qquad \uc\uc\dc\ec,
\end{equation}
and the sterile-neutrino branch includes
\begin{equation}
  \uc\dc\dc\nuc.
\end{equation}
All of these preserve $B-L$ in the P1 bookkeeping.

The physical proton-bound interface is recorded as
\begin{equation}
  \Gamma(p\to a)
  =
  \sum_{i,j}
  C_i^{\rm phys}\,
  C_j^{\rm phys\,\ast}\,
  H_{ij}^{(a)},
\end{equation}
where $H_{ij}^{(a)}$ contains phase space, RG evolution, chiral reduction, and
hadronic matrix elements for channel $a$.  A lifetime lower bound implies
\begin{equation}
  (C^{\rm phys})^\dagger H^{(a)} C^{\rm phys}
  <
  \frac{1}{\tau_a^{\rm exp}}.
\end{equation}
For a single coefficient this reduces schematically to
\begin{equation}
  |C_i^{\rm phys}|
  <
  \sqrt{\frac{1}{\tau_a^{\rm exp}H_{ii}^{(a)}}}.
\end{equation}

P7 deliberately does not insert numerical proton limits.  Numerical
lifetimes require:
\begin{equation}
\begin{gathered}
  \text{P6-completed high-energy branch},\quad
  \text{mediator masses and couplings},\quad
  \text{physical flavor rotations},\\
  \text{operator basis and chiral contractions},\quad
  \text{RG factors},\quad
  \text{lattice/chiral matrix elements},\quad
  \tau_a^{\rm exp}.
\end{gathered}
\end{equation}
Thus P7 is a proton-bound readiness report, not a proton-lifetime
calculation.

\section{P8: Comparative Theory Scorecard}

P8 compares candidate branches using the explicit P1--P7 gates.  It is a
hard-gate ledger, not a subjective weighted score.  The gates are:
\begin{center}
\small
\begin{tabular}{
  >{\raggedright\arraybackslash}p{0.12\linewidth}
  >{\raggedright\arraybackslash}p{0.72\linewidth}}
C0 & representation pre-filter\\
P1 & charge/anomaly baseline\\
P2 & charge-filtered pole ledger\\
P3 & residue factorization/PSD\\
P4 & Ward-completion readiness\\
P5 & anomaly/chiral/exotics ledger\\
P6 & high-energy-growth completion gate\\
P7 & proton-bound readiness
\end{tabular}
\end{center}

The generated P8 scorecard compares five candidates.  Its leading conditional
finite field-theory branch is $\Spin(10)$, and it does not yet force a
tower-like UV completion.
The candidate verdicts are:
\begin{center}
\small
\begin{tabular}{
  >{\raggedright\arraybackslash}p{0.24\linewidth}
  >{\raggedright\arraybackslash}p{0.64\linewidth}}
\toprule
candidate & P8 verdict \\
\midrule
$\SU(5)$ &
conditional branch if the single-object filter is relaxed; anomaly-consistent
but family-split as $10\oplus\bar 5\oplus 1$ \\
Pati--Salam &
conditional intermediate face; natural and anomaly-consistent, but product
group and not one simple single-object branch \\
$\Spin(10)$ &
leading conditional finite field-theory branch under the current minimal
single-object filter; still has action-level and proton-bound completion debt\\
$E_6$ &
conditional branch with exotics-lifting debt from $27\to16\oplus10\oplus1$ \\
superstring-derived completions &
UV-completion class, not forced by P1--P7; serious comparison branch if
finite-pole completions fail \\
\bottomrule
\end{tabular}
\end{center}

Thus P8 closes the first Route C pass as a comparative filter:
\begin{equation}
  \Spin(10)
  =
  \text{leading conditional finite branch},
  \qquad
  \text{not a completed GUT proof}.
\end{equation}
Superstring-derived completions remain comparison branches, not P8
conclusions.

\section{P9: Spin(10)-Locked Action-Completion Data}

P9 stops broadening the candidate comparison and locks the finite
field-theory branch to the P8-leading $\Spin(10)$ option.  The generated
ledger uses the Pati--Salam decomposition
\begin{equation}
  16
  \longrightarrow
  (4,2,1)\oplus(\bar 4,1,2),
\end{equation}
and builds a sparse sixteen-state basis for
\begin{equation}
  Q\oplus L\oplus\uc\oplus\dc\oplus\nuc\oplus\ec .
\end{equation}
The broken-generator data are represented as sparse transition maps rather
than as a completed Lagrangian.  P9 reports:
\begin{center}
\small
\begin{tabular}{p{0.58\linewidth}r}
\toprule
quantity & value\\
\midrule
basis dimension & 16\\
broken generator sparse maps & 32\\
$\SU(4)_C$ leptoquark root maps & 6\\
broken $\SU(2)_R$ charged root maps & 2\\
$\Spin(10)/$Pati--Salam $(6,2,2)$ Clebsch maps & 24\\
P4 broken transition pairs & 30\\
$\Spin(10)$ adjoint vector transition pairs & 22\\
non-adjoint P4 completion pairs & 8\\
P9 generator layer passes & true\\
\bottomrule
\end{tabular}
\end{center}

The important refinement is that not every P4 charge-bookkeeping transition
is a $\Spin(10)$ adjoint gauge vector.  The eight non-adjoint P4 pairs are
not generator failures; they remain scalar, source, or auxiliary completion
candidates if a later branch activates them.  P9 therefore supplies the
generator layer without pretending that charge-allowed transitions are
automatically $D_5$ gauge generators.

For every broken vector, the action-level Ward target remains
\begin{equation}
  p_\mu{\cal M}^\mu(V_X)=M_X{\cal M}(\phi_X).
\end{equation}
P9 records the corresponding completion templates for
\begin{equation}
  \Spin(10)\to \text{Pati--Salam},\qquad
  \SU(4)_C\to\SU(3)_C\times U(1)_{B-L},\qquad
  \SU(2)_R\to U(1)_{T3R}.
\end{equation}
It also records the still-symbolic inputs
\begin{equation}
  g_{10},\quad M_{(6,2,2)},\quad M_{\rm LQ},\quad M_{W_R},
\end{equation}
plus the physical flavor rotations and proton-bound interface.  Thus P9 is
an action-completion interface, not yet a spectrum choice, flavor fit, or
proton-lifetime calculation.

\section{P10: Spin(10) Breaking Mass Matrix}

P10 chooses the conservative staged branch
\begin{equation}
\begin{gathered}
  \Spin(10)\to \SU(4)_C\times\SU(2)_L\times\SU(2)_R,\\
  \SU(4)_C\to \SU(3)_C\times U(1)_{B-L},\qquad
  \SU(2)_R\to U(1)_{T3R},\\
  U(1)_{T3R}\times U(1)_{B-L}\to U(1)_Y .
\end{gathered}
\end{equation}
The branch is a source-level mass model, not a complete Higgs potential.  It
is chosen because it turns the P9 symbolic inputs into positive blocks while
preserving the hypercharge zero mode.

The resulting active vector mass matrix has the block form
\begin{equation}
  M^2_{\rm active}
  =
  \diag\left(
    M_{(6,2,2)}^2 I_{24},
    M_{\rm LQ}^2 I_6,
    M_{W_R}^2 I_2,
    M_{\rm neutral}^2
  \right),
\end{equation}
where
\begin{equation}
  M_{(6,2,2)}^2=\kappa_{\rm PS}g_{10}^2v_{\rm PS}^2,
  \qquad
  M_{\rm LQ}^2=\frac23 g_4^2v_4^2,
  \qquad
  M_{W_R}^2=g_R^2v_R^2.
\end{equation}
The leptoquark coefficient follows from the normalized generator
\begin{equation}
  T_{B-L}
  =
  \sqrt{\frac38}\,
  \diag\left(\frac13,\frac13,\frac13,-1\right),
  \qquad
  (\Delta T_{B-L})^2=\frac23 .
\end{equation}
For the neutral sector, a $Y=0$ $\nuc$-like source with charges
$q_R=-1/2$ and $q_{B-L}/2=+1/2$ gives
\begin{equation}
  M_{\rm neutral}^2
  =
  \frac{v_Y^2}{4}
  \begin{pmatrix}
    g_R^2 & -g_Rg_{BL}\\
    -g_Rg_{BL} & g_{BL}^2
  \end{pmatrix}_{(W_R^3,B_{B-L})}.
\end{equation}
This matrix has eigenvalues
\begin{equation}
  0,\qquad
  \frac{v_Y^2}{4}(g_R^2+g_{BL}^2),
\end{equation}
with massless hypercharge direction
\begin{equation}
  B_Y\propto g_{BL}W_R^3+g_RB_{B-L},
  \qquad
  g_Y=\frac{g_Rg_{BL}}{\sqrt{g_R^2+g_{BL}^2}}.
\end{equation}
In the unit demo point
\begin{equation}
  g_{10}=g_4=g_R=g_{BL}=v_{\rm PS}=v_4=v_R=v_Y=1,
  \qquad
  \kappa_{\rm PS}=1,
\end{equation}
P10 finds a $34$-dimensional active matrix, $33$ positive broken eigenvalues,
and one zero eigenvalue.  This is the expected count for
\begin{equation}
  \dim\Spin(10)-\dim G_{\rm SM}=45-12=33.
\end{equation}
The remaining physical inputs are the scale choices, scalar/source branch for
the eight non-adjoint P4 pairs if activated, physical flavor rotations, RG
factors, hadronic matrix elements, and experimental proton lifetime limits.

\section{P11: Replay with Staged Spin(10) Masses}

P11 attaches the P10 mass blocks to the matching gates:
\begin{equation}
\begin{gathered}
  M_{(6,2,2)}\to \sqrt{\kappa_{\rm PS}}\,g_{10}v_{\rm PS},\\
  M_{\rm LQ}\to \sqrt{\frac23}\,g_4v_4,\qquad
  M_{W_R}\to g_Rv_R,\\
  M_{Z'}\to \frac12 v_Y\sqrt{g_R^2+g_{BL}^2}.
\end{gathered}
\end{equation}
The current-vector side is therefore improved: the adjoint-vector sectors now
carry explicit staged denominators.  However, P11 also checks the P7
chiral-pair pole rows against the adjoint-current charge signatures.  The
result is:
\begin{center}
\small
\begin{tabular}{p{0.62\linewidth}r}
\toprule
quantity & value\\
\midrule
current-vector mass blocks available & 4\\
P7 rows replayed & 18\\
P7 rows with candidate adjoint mass blocks & 0\\
P7 rows remaining scalar/source mass debt & 18\\
baryon-violating or sterile-BNV rows & 6\\
physical proton bounds evaluable now & 0\\
\bottomrule
\end{tabular}
\end{center}
This is a negative but useful gate: the P7 all-incoming chiral-pair pole
ledger is not automatically the same as adjoint current-vector exchange.  Thus
P11 does not unlock proton bounds.  It says that the next Wilson-basis choice
is unavoidable:
\begin{equation}
  \text{current-current vector branch}
  \quad\text{or}\quad
  \text{scalar/source chiral-pair branch}.
\end{equation}
The two branches require different spin/channel maps before numerical proton
limits can be inserted.

\section{P12-S: Scalar/Source Chiral-Pair Branch}

P12 records both post-P11 directions:
\begin{equation}
  \text{Branch V}=\text{completed }\Spin(10)\text{ current-current vector exchange},
\end{equation}
and
\begin{equation}
  \text{Branch S}=\text{scalar/source chiral-pair poles}.
\end{equation}
Both directions remain part of the Route C program.  The first activated
direction is Branch S, because P11 found that all P7 chiral-pair rows remain
scalar/source mass debt rather than adjoint-vector matches.

The scalar/source ansatz is
\begin{equation}
  \mathcal L
  \supset
  \lambda_{ab,R}\psi_a\psi_b S_R
  +\mathrm{h.c.}
  +M_{S_R}^2 |S_R|^2,
  \qquad M_{S_R}^2>0 .
\end{equation}
Integrating out the scalar/source field at tree level gives the symbolic
dimension-six coefficient
\begin{equation}
  C_6(12|34;R)
  =
  \frac{\lambda_{12,R}\lambda_{34,R}^{\ast}}{M_{S_R}^2}.
\end{equation}
This avoids the longitudinal broken-vector Ward problem, but it does not
prove a UV completion or a physical proton lifetime.

The generated P12-S ledger reports:
\begin{center}
\small
\begin{tabular}{p{0.64\linewidth}r}
\toprule
quantity & value\\
\midrule
P11 scalar/source debt rows converted & 18\\
unique scalar/source sectors & 12\\
$B$ and $L$ conserving rows & 12\\
standard BNV seed rows & 4\\
BNV-with-sterile-neutrino rows & 2\\
baryon-violating or sterile-BNV rows & 6\\
physical proton bounds evaluable now & 0\\
\bottomrule
\end{tabular}
\end{center}
The six baryon-violating or sterile-BNV scalar/source rows are the two
$QQQL$ rows, the two $\uc\uc\dc\ec$ rows, and the two
$\uc\dc\dc\nuc$ rows.  Their coefficients remain symbolic because P12-S has
not chosen the scalar/source flavor tensors or the physical Wilson basis.

The verification checks are:
\begin{center}
\small
\begin{tabular}{p{0.68\linewidth}c}
\toprule
check & result\\
\midrule
all P11 scalar/source debt rows accounted for & true\\
every scalar/source row has a mass symbol & true\\
every source sector has a positive mass condition & true\\
P12 scalar/source layer passes & true\\
\bottomrule
\end{tabular}
\end{center}

The next scalar/source stage is therefore not a proton-bound insertion.  It is
the construction of scalar/source flavor tensors and a chiral/Fierz Wilson
basis for the BNV rows.  The parallel completed current-current vector branch
also remains open and should be tried before any final proton-bound claim is
made.

\section{Current Status and Next Check}

The P1--P12-S chain currently establishes:
\begin{enumerate}
\item the exact P1 charge/anomaly baseline for one $SM+\nuc$ family;
\item the P2 charge-filtered symbolic pole components;
\item the P3 conditional residue-factorization and PSD statement;
\item the P4 Ward-identity completion ledger for broken/off-face sectors;
\item the P5 anomaly/chiral-consistency comparison across candidate branches.
\item the P6 high-energy-growth ledger for finite-vector, scalar/auxiliary,
contact-only, and tower-like comparison branches.
\item the P7 conditional low-energy matching and proton-bound readiness
ledger.
\item the P8 comparative scorecard across $\SU(5)$, Pati--Salam, $\Spin(10)$,
$E_6$, and superstring-derived completions.
\item the P9 $\Spin(10)$-locked sparse generator ledger and action-completion
interface.
\item the P10 staged $\Spin(10)$ breaking mass matrix with $33$ positive
broken-vector eigenvalues and one hypercharge zero mode.
\item the P11 replay gate showing that P10 supplies adjoint-vector mass
denominators, while the P7 chiral-pair rows remain scalar/source mass debt.
\item the P12-S scalar/source branch that assigns symbolic scalar/source
denominators to all 18 P7 chiral-pair rows, with 12 source sectors and 6 BNV
or sterile-BNV rows still awaiting flavor/Wilson-basis data.
\end{enumerate}
The next natural stage is P13: choose scalar/source flavor tensors and a
chiral/Fierz Wilson basis for the six BNV or sterile-BNV rows, or return to
the parallel completed current-current vector branch before inserting proton
limits.

\end{document}
